---
title: "Case Study"
author: "Group-14"
runtime: shiny
output: html_document
---

```{r Load Required Packages, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

#Kindly go to "Edit>Folding>Collpase all" to fold all the code chunks, to make the code better readable.

if (!require(data.table)) {
  install.packages("data.table")
  require(data.table)
}
if (!require(readr)) {
  install.packages("readr")
  require(readr)
}
if (!require(readxl)) {
  install.packages("readxl")
  require(readxl)
}
if (!require(dplyr)) {
  install.packages("dplyr")
  require(dplyr)
}
if (!require(tidyr)) {
  install.packages("tidyr")
  require(tidyr)
}
if (!require(purrr)) {
  install.packages("purrr")
  require(purrr)
}
if (!require(stringr)) {
  install.packages("stringr")
  require(stringr)
}
if (!require(rebus)) {
  install.packages("rebus")
  require(rebus)
}
if (!require(tidyverse)) {
  install.packages("tidyverse")
  require(tidyverse)
}
if (!require(ggplot2)) {
  install.packages("ggplot2")
  require(ggplot2)
}
if (!require(ggQC)) {
  install.packages("ggQC")
  require(ggQC)
}
if (!require(shiny)) {
  install.packages("shiny")
  require(shiny)
}
if (!require(plotly)) {
  install.packages("plotly")
  require(shiny)
}
```
```{r Load Required Packages ONLY FOR SHINY APP, message=FALSE, warning=FALSE, include=FALSE}

#Kindly go to "Edit>Folding>Collpase all" to fold all the code chunks, to make the code better readable.

if (!require(shiny)) {
  install.packages("shiny")
  require(shiny)
}
if (!require(plotly)) {
  install.packages("plotly")
  require(shiny)
}
```

```{r Importing Cleaning and Manipulating Data, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

#Kindly go to "Edit>Folding>Collpase all" to fold all the code chunks, to make the code better readable.


#data is read in and checked to clean all IDS are renamed to be able to match by column names
renameIDs <- c("ID_Motor"= "ID_Komponente", "ID_Schaltung"= "ID_Komponente", "ID_Karosserie"= "ID_Komponente", "ID_Sitze"= "ID_Komponente", "Produktionsdatum_Origin_01011970" = "Produktionsdatum")

Komponente26 <- fread("Data/Komponente/Komponente_K1BE1.csv")
Komponente26$origin <- as.Date(Komponente26$origin, format = "%d-%m-%Y")
Komponente26 <- transform(Komponente26, Produktionsdatum = Komponente26$Produktionsdatum_Origin_01011970 + Komponente26$origin) #Production Date is found by adding these two columns
Komponente26$Produktionsdatum_Origin_01011970<- NULL
Komponente26$origin<- NULL
Komponente26$V1 <- NULL
Komponente26$X1 <- NULL
Komponente26$Fehlerhaft_Fahrleistung <- NULL
Komponente26 <- plyr::rename(Komponente26, renameIDs)

Komponente27 <- fread("Data/Komponente/Komponente_K1BE2.csv")
Komponente27$Fehlerhaft_Datum <- as.Date(Komponente27$Fehlerhaft_Datum, format = "%Y-%m-%d")
Komponente27$origin <- as.Date(Komponente27$origin, format = "%d-%m-%Y")
Komponente27 <- transform(Komponente27, Produktionsdatum = Komponente27$Produktionsdatum_Origin_01011970 + Komponente27$origin)
Komponente27$Produktionsdatum_Origin_01011970<- NULL
Komponente27$origin<- NULL
Komponente27$V1 <- NULL
Komponente27$X1 <- NULL
Komponente27$Fehlerhaft_Fahrleistung <- NULL
Komponente27 <- plyr::rename(Komponente27, renameIDs)


Komponente28 <- fread("Data/Komponente/Komponente_K1DI1.csv")
Komponente28$Produktionsdatum.x  <- as.Date(Komponente28$Produktionsdatum.x, format = "%Y-%m-%d")
Komponente28$Produktionsdatum.y  <- as.Date(Komponente28$Produktionsdatum.y, format = "%Y-%m-%d")
Komponente28$Produktionsdatum  <- as.Date(Komponente28$Produktionsdatum, format = "%Y-%m-%d")
Komponente28$V1<- NULL
Komponente28$X1<- NULL
x <-  filter(Komponente28, !is.na(`Produktionsdatum.y` ))
x <- select(x, ID_Motor.y, `Produktionsdatum.y`, `Herstellernummer.y`, `Werksnummer.y`, `Fehlerhaft.y`, `Fehlerhaft_Datum.y`)
x2 <-  filter(Komponente28, !is.na(`Produktionsdatum.x` ))
x2 <- select(x2, ID_Motor.x,`Produktionsdatum.x`, `Herstellernummer.x`, `Werksnummer.x`, `Fehlerhaft.x`, `Fehlerhaft_Datum.x`)
x3 <-  filter(Komponente28, !is.na(`Produktionsdatum` ))
x3 <- select(x3, ID_Motor,`Produktionsdatum`, `Herstellernummer`, `Werksnummer`, `Fehlerhaft`, `Fehlerhaft_Datum`)
rename.x <- c("ID_Motor.x" = "ID_Motor","ID_Sitze.x" = "ID_Sitze", "ID_Schaltung.x" = "ID_Schaltung", "Produktionsdatum.x" = "Produktionsdatum", "Herstellernummer.x"= "Herstellernummer", "Werksnummer.x" = "Werksnummer", "Fehlerhaft.x" = "Fehlerhaft", "Fehlerhaft_Datum.x" = "Fehlerhaft_Datum", "ID_Karosserie.x"= "ID_Karosserie")
rename.y <- c("ID_Motor.y" = "ID_Motor","ID_Sitze.y" = "ID_Sitze", "ID_Schaltung.y" = "ID_Schaltung", "Produktionsdatum.y" = "Produktionsdatum", "Herstellernummer.y"= "Herstellernummer", "Werksnummer.y" = "Werksnummer", "Fehlerhaft.y" = "Fehlerhaft", "Fehlerhaft_Datum.y" = "Fehlerhaft_Datum", "ID_Karosserie.y"= "ID_Karosserie")
x <- plyr::rename(x, rename.y)
x2 <- plyr::rename(x2, rename.x)
Komponente28 <- bind_rows(x,x2,x3)
Komponente28 <- plyr::rename(Komponente28, renameIDs)


Komponente29 <- read_file("Data/Komponente/Komponente_K1DI2.txt")
Komponente29<-str_split(Komponente29,pattern="\\\"[0-9]+\"\\\\[0-9]+\\\\\\\"")
Komponente29 <- data.frame(Komponente29)
Komponente29 <- separate(Komponente29, col=1, sep = "\\\\", into = c("ID_Motor","Herstellernummer","Werksnummer","Fehlerhaft","Fehlerhaft_Datum","Fehlerhaft_Fahrleistung","Produktionsdatum_Origin_01011970","origin"))
Komponente29 <- Komponente29[-1,]
Komponente29$Produktionsdatum_Origin_01011970 <- as.Date(as.POSIXct(origin = "1970-01-01", as.numeric((Komponente29$Produktionsdatum_Origin_01011970))*86400))
Komponente29 <- select(Komponente29, "ID_Motor","Herstellernummer","Werksnummer","Fehlerhaft","Fehlerhaft_Datum","Fehlerhaft_Fahrleistung","Produktionsdatum_Origin_01011970")
Komponente29$Fehlerhaft_Fahrleistung <- NULL
Komponente29$ID_Sitze <- str_remove_all(Komponente29$ID_Motor,"\"")
Komponente29 <- plyr::rename(Komponente29, renameIDs)
Komponente29$ID_Komponente <- str_remove_all(Komponente29$ID_Komponente,"\"")
Komponente29$Werksnummer <- str_remove_all(Komponente29$Werksnummer,"\"")
Komponente29$Werksnummer <- as.integer(Komponente29$Werksnummer)
Komponente29$Fehlerhaft <- as.integer(Komponente29$Fehlerhaft)
#same problem and approach as with Komponente28
Komponente30 <-read_file("Data/Komponente/Komponente_K2LE1.txt")
Komponente30<-str_split(Komponente30, pattern="_")
Komponente30<-data.frame(Komponente30)
Komponente30<-separate(Komponente30, col = 1, sep = "II", into = c("X1", "X2","ID_Sitze.x","Produktionsdatum.x","Herstellernummer.x","Werksnummer.x","Fehlerhaft.x","Fehlerhaft_Datum.x","Fehlerhaft_Fahrleistung.x", "ID_Sitze.y","Produktionsdatum.y","Herstellernummer.y","Werksnummer.y","Fehlerhaft.y","Fehlerhaft_Datum.y", "Fehlerhaft_Fahrleistung.y"))
#next step filter for empty rows and rejoin
Komponente30 <- Komponente30[-1,]
Komponente30$Produktionsdatum.x  <- as.Date(Komponente30$Produktionsdatum.x, format = "%Y-%m-%d")
Komponente30$Produktionsdatum.y  <- as.Date(Komponente30$Produktionsdatum.y, format = "%Y-%m-%d")
head(Komponente30)
Komponente30$X1 <- NULL
Komponente30$X2 <- NULL
#filtering and splitting because some data is saved as .x and some as .y
x <-  filter(Komponente30, !is.na(`Produktionsdatum.y` ))
x <- select(x, ID_Sitze.y, `Produktionsdatum.y`, `Herstellernummer.y`, `Werksnummer.y`, `Fehlerhaft.y`, `Fehlerhaft_Datum.y`)
x2 <-  filter(Komponente30, !is.na(`Produktionsdatum.x` ))
x2 <- select(x2, `ID_Sitze.x`, `Produktionsdatum.x`, `Herstellernummer.x`, `Werksnummer.x`, `Fehlerhaft.x`, `Fehlerhaft_Datum.x`)
#rename to be able to use bind rows to be able to bind the komponent data all together
x <- plyr::rename(x, rename.y)
x2 <- plyr::rename(x2, rename.x)
Komponente30 <- bind_rows(x,x2)
Komponente30 <- plyr::rename(Komponente30, renameIDs)
Komponente30$ID_Komponente <- str_remove_all(Komponente30$ID_Komponente,"\"")
Komponente30$Werksnummer <- as.integer(Komponente30$Werksnummer)
Komponente30$Fehlerhaft <- as.integer(Komponente30$Fehlerhaft)


Komponente31 <- read_file("Data/Komponente/Komponente_K2LE2.txt")
Komponente31<-str_split(Komponente31,pattern="\r")
Komponente31 <- data.frame(Komponente31)
Komponente31 <- separate(Komponente31, col = 1, sep = "\\\\", into = c("X1","X11","ID_Sitze","Herstellernummer","Werksnummer","Fehlerhaft","Fehlerhaft_Datum", "Fehlerhaft_Fahrleistung", "Produktionsdatum_Origin_01011970", "origin"))
Komponente31 <- Komponente31[-1,]
Komponente31$X1 <- NULL
Komponente31$X11 <- NULL
Komponente31$origin <- NULL
Komponente31$Produktionsdatum_Origin_01011970 <- as.Date(as.POSIXct(origin = "1970-01-01", as.numeric((Komponente31$Produktionsdatum_Origin_01011970))*86400))
Komponente31$ID_Sitze <- str_remove_all(Komponente31$ID_Sitze,"\"") #To remove all Quotes from the Column
Komponente31$Herstellernummer <- str_remove_all(Komponente31$Herstellernummer,"\"") #To remove all Quotes from the Column
Komponente31$Werksnummer <- str_remove_all(Komponente31$Werksnummer,"\"") #To remove all Quotes from the Column
Komponente31 <- plyr::rename(Komponente31, renameIDs)
Komponente31$Fehlerhaft_Fahrleistung <- NULL
Komponente31$Werksnummer <- as.integer(Komponente31$Werksnummer)
Komponente31$Fehlerhaft <- as.integer(Komponente31$Fehlerhaft)


Komponente32 <- fread("Data/Komponente/Komponente_K2ST1.txt")
Komponente32$Produktionsdatum <- as.Date(Komponente32$Produktionsdatum)
Komponente32$V1 <- NULL
Komponente32$X1 <- NULL
Komponente32$Fehlerhaft_Fahrleistung <- NULL
Komponente32 <- plyr::rename(Komponente32, renameIDs)


Komponente33 <- fread("Data/Komponente/Komponente_K2ST2.csv")
Komponente33$V1 <- NULL
Komponente33$X1 <- NULL
Komponente33$Produktionsdatum_Origin_01011970 <- as.Date(as.POSIXct(origin = "1970-01-01", as.numeric((Komponente33$Produktionsdatum_Origin_01011970))*86400))
Komponente33$origin <- NULL
Komponente33$Fehlerhaft_Fahrleistung <- NULL
Komponente33 <- plyr::rename(Komponente33, renameIDs)


Komponente34 <- fread("Data/Komponente/Komponente_K3AG1.csv")
#file is spilt in 3 different columns and respective NAS. Procedure from Komponente 28 is adapted
x <-  filter(Komponente34, !is.na(`Produktionsdatum.y` ))
x <- select(x, ID_Schaltung.y, `Produktionsdatum.y`, `Herstellernummer.y`, `Werksnummer.y`, `Fehlerhaft.y`, `Fehlerhaft_Datum.y`)
x2 <-  filter(Komponente34, !is.na(`Produktionsdatum.x` ))
x2 <- select(x2, ID_Schaltung.x,`Produktionsdatum.x`, `Herstellernummer.x`, `Werksnummer.x`, `Fehlerhaft.x`, `Fehlerhaft_Datum.x`)
x3 <-  filter(Komponente34, !is.na(`Produktionsdatum` ))
x3 <- select(x3, ID_Schaltung,`Produktionsdatum`, `Herstellernummer`, `Werksnummer`, `Fehlerhaft`, `Fehlerhaft_Datum`)
x <- plyr::rename(x, rename.y)
x2 <- plyr::rename(x2, rename.x)
Komponente34 <- bind_rows(x,x2,x3)
Komponente34$Produktionsdatum <- as.Date(Komponente34$Produktionsdatum)
Komponente34 <- plyr::rename(Komponente34, renameIDs)


Komponente35 <- read_file("Data/Komponente/Komponente_K3AG2.txt")
Komponente35 <- str_split(Komponente35,pattern="\\\"[0-9]+\"\\\\[0-9]+\\\\\\\"")
Komponente35 <- data.frame(Komponente35)
Komponente35<-separate(Komponente35, col = 1, sep = "\\\\", into = c("ID_Schaltung","Herstellernummer","Werksnummer","Fehlerhaft","Fehlerhaft_Datum","Fehlerhaft_Fahrleistung","Produktionsdatum_Origin_01011970","origin"))
Komponente35$Produktionsdatum_Origin_01011970  <- as.Date(as.POSIXct(origin = "1970-01-01", as.numeric((Komponente35$Produktionsdatum_Origin_01011970))*86400))
Komponente35$origin <- NULL
Komponente35 <- plyr::rename(Komponente35, renameIDs)
Komponente35$Fehlerhaft_Fahrleistung <- NULL
Komponente35 <- Komponente35[-1,]
Komponente35$ID_Komponente <- str_remove_all(Komponente35$ID_Komponente,"\"")
Komponente35$Werksnummer <- str_remove_all(Komponente35$Werksnummer,"\"")
Komponente35$Werksnummer <- as.integer(Komponente35$Werksnummer)
Komponente35$Fehlerhaft <- as.integer(Komponente35$Fehlerhaft)


Komponente36 <- fread("Data/Komponente/Komponente_K3SG1.csv")
Komponente36$V1<- NULL
Komponente36$X1<- NULL
Komponente36$Fehlerhaft_Datum.x <- as.Date(Komponente36$Fehlerhaft_Datum.x, format = "%Y-%m-%d")
Komponente36$Fehlerhaft_Datum.y <- as.Date(Komponente36$Fehlerhaft_Datum.y, format = "%Y-%m-%d")
#same problem as with Komonente 28 but only split in two, therefore same procedure is applied
x <-  filter(Komponente36, !is.na(`Produktionsdatum.y` ))
x <- select(x, ID_Schaltung.y, `Produktionsdatum.y`, `Herstellernummer.y`, `Werksnummer.y`, `Fehlerhaft.y`, `Fehlerhaft_Datum.y`)
x2 <-  filter(Komponente36, !is.na(`Produktionsdatum.x` ))
x2 <- select(x2, ID_Schaltung.x,`Produktionsdatum.x`, `Herstellernummer.x`, `Werksnummer.x`, `Fehlerhaft.x`, `Fehlerhaft_Datum.x`)
x <- plyr::rename(x, rename.y)
x2 <- plyr::rename(x2, rename.x)
Komponente36 <- bind_rows(x,x2)
Komponente36$Produktionsdatum <- as.Date(Komponente36$Produktionsdatum)
Komponente36 <- plyr::rename(Komponente36, renameIDs)


Komponente37 <- fread("Data/Komponente/Komponente_K3SG2.csv")
Komponente37$V1<- NULL
Komponente37$X1<- NULL
Komponente37$origin <- as.Date(Komponente37$origin, format = "%d-%m-%Y")
Komponente37 <- transform(Komponente37, Produktionsdatum = Komponente37$Produktionsdatum_Origin_01011970 + Komponente37$origin)
Komponente37$Produktionsdatum_Origin_01011970<- NULL
Komponente37$origin<- NULL
head(Komponente37)
Komponente37 <- plyr::rename(Komponente37, renameIDs)
Komponente37$Fehlerhaft_Fahrleistung <- NULL


Komponente38 <- fread("Data/Komponente/Komponente_K4.csv")
Komponente38$V1<- NULL
Komponente38$X1<- NULL
x <-  filter(Komponente38, !is.na(`Produktionsdatum.y` ))
x <- select(x, ID_Karosserie.y, `Produktionsdatum.y`, `Herstellernummer.y`, `Werksnummer.y`, `Fehlerhaft.y`, `Fehlerhaft_Datum.y`)
x2 <-  filter(Komponente38, !is.na(`Produktionsdatum.x` ))
x2 <- select(x2, ID_Karosserie.x,`Produktionsdatum.x`, `Herstellernummer.x`, `Werksnummer.x`, `Fehlerhaft.x`, `Fehlerhaft_Datum.x`)
x <- plyr::rename(x, rename.y)
x2 <- plyr::rename(x2, rename.x)
Komponente38 <- bind_rows(x,x2)
Komponente38$Fehlerhaft_Fahrleistung <- NULL
Komponente38$Produktionsdatum <- as.Date(Komponente38$Produktionsdatum)
Komponente38 <- plyr::rename(Komponente38, renameIDs)


Komponente39 <- fread("Data/Komponente/Komponente_K5.csv")
x <-  filter(Komponente39, !is.na(`Produktionsdatum.y` ))
x <- select(x, ID_Karosserie.y, `Produktionsdatum.y`, `Herstellernummer.y`, `Werksnummer.y`, `Fehlerhaft.y`, `Fehlerhaft_Datum.y`)
x2 <-  filter(Komponente39, !is.na(`Produktionsdatum.x` ))
x2 <- select(x2, ID_Karosserie.x,`Produktionsdatum.x`, `Herstellernummer.x`, `Werksnummer.x`, `Fehlerhaft.x`, `Fehlerhaft_Datum.x`)
x <- plyr::rename(x, rename.y)
x2 <- plyr::rename(x2, rename.x)
Komponente39 <- bind_rows(x,x2)
Komponente39$Produktionsdatum <- as.Date(Komponente39$Produktionsdatum)
Komponente39 <- plyr::rename(Komponente39, renameIDs)


Komponente40 <- fread("Data/Komponente/Komponente_K6.csv")
Komponente40$X1 <- NULL
Komponente40$V1 <- NULL
Komponente40$origin <- as.Date(Komponente40$origin, format = "%d-%m-%Y")
Komponente40 <- transform(Komponente40, Produktionsdatum = Komponente40$Produktionsdatum_Origin_01011970 + Komponente40$origin)
Komponente40$Produktionsdatum_Origin_01011970<- NULL
Komponente40$origin <- NULL
Komponente40$Fehlerhaft_Fahrleistung <- NULL
Komponente40 <- plyr::rename(Komponente40, renameIDs)


Komponente41 <- fread("Data/Komponente/Komponente_K7.txt")
Komponente41$origin <- as.Date(Komponente41$origin, format = "%d-%m-%Y")
Komponente41 <- transform(Komponente41, Produktionsdatum = Komponente41$Produktionsdatum_Origin_01011970 + Komponente41$origin)
Komponente41$Produktionsdatum_Origin_01011970<- NULL
Komponente41$origin<- NULL
Komponente41$X1 <- NULL
Komponente41$V1 <- NULL
Komponente41$Fehlerhaft_Fahrleistung <- NULL
Komponente41 <- plyr::rename(Komponente41, renameIDs)


#bind all Komponentstogether
Komponente41$Fehlerhaft_Datum <- NULL
Komponente40$Fehlerhaft_Datum <- NULL
Komponente39$Fehlerhaft_Datum <- NULL 
Komponente38$Fehlerhaft_Datum <- NULL
Komponente37$Fehlerhaft_Datum <- NULL
Komponente36$Fehlerhaft_Datum <- NULL 
Komponente35$Fehlerhaft_Datum <- NULL 
Komponente34$Fehlerhaft_Datum <- NULL
Komponente33$Fehlerhaft_Datum <- NULL
Komponente32$Fehlerhaft_Datum <- NULL
Komponente31$Fehlerhaft_Datum <- NULL
Komponente30$Fehlerhaft_Datum <- NULL
Komponente29$Fehlerhaft_Datum <- NULL
Komponente28$Fehlerhaft_Datum <- NULL
Komponente27$Fehlerhaft_Datum <- NULL
Komponente26$Fehlerhaft_Datum <- NULL
Komponente41$Herstellernummer <- NULL
Komponente40$Herstellernummer <- NULL
Komponente39$Herstellernummer <- NULL 
Komponente38$Herstellernummer <- NULL
Komponente37$Herstellernummer <- NULL
Komponente36$Herstellernummer <- NULL 
Komponente35$Herstellernummer <- NULL 
Komponente34$Herstellernummer <- NULL
Komponente33$Herstellernummer <- NULL
Komponente32$Herstellernummer <- NULL
Komponente31$Herstellernummer <- NULL
Komponente30$Herstellernummer <- NULL
Komponente29$Herstellernummer <- NULL
Komponente28$Herstellernummer <- NULL
Komponente27$Herstellernummer <- NULL
Komponente26$Herstellernummer <- NULL
Komponente28 <- Komponente28[,c(1,3,4,2)]
Komponente29 <- Komponente29[,c(5,2,3,4)]
Komponente30 <- Komponente30[,c(1,3,4,2)]
Komponente32 <- Komponente32[,c(1,3,4,2)]
Komponente34 <- Komponente34[,c(1,3,4,2)]
Komponente36 <- Komponente36[,c(1,3,4,2)]
Komponente38<- Komponente38[,c(1,3,4,2)]
Komponente39 <- Komponente39[,c(1,3,4,2)]
Komponents_all <- bind_rows(Komponente41, Komponente40, Komponente39, Komponente38, Komponente37, Komponente36, Komponente35, Komponente34, Komponente33, Komponente32, Komponente31, Komponente30, Komponente29, Komponente28, Komponente27, Komponente26)
Komponents_all <- na.omit(Komponents_all)

#Extract only the Years
rm(list = ls(pattern="Komponente")) #remove unnecessary variables
rm(list = ls(pattern="x"))
rm(list = ls(pattern="rename"))

#change Component Names to a Simpler Fromat necessary for the Final Plots
Komponents_all[str_detect(Komponents_all$ID_Komponente,"^K6")]$ID_Komponente <- "K6"
Komponents_all[str_detect(Komponents_all$ID_Komponente,"^K7")]$ID_Komponente <- "K7"
Komponents_all[str_detect(Komponents_all$ID_Komponente,"^K5")]$ID_Komponente <- "K5"
Komponents_all[str_detect(Komponents_all$ID_Komponente,"^K4")]$ID_Komponente <- "K4"
Komponents_all[str_detect(Komponents_all$ID_Komponente,"^K3SG2-")]$ID_Komponente <- "K3SG2"
Komponents_all[str_detect(Komponents_all$ID_Komponente,"^K3SG1-")]$ID_Komponente <- "K3SG1"
Komponents_all[str_detect(Komponents_all$ID_Komponente,"^K3AG2-")]$ID_Komponente <- "K3AG2"
Komponents_all[str_detect(Komponents_all$ID_Komponente,"^K3AG1-")]$ID_Komponente <- "K3AG1"
Komponents_all[str_detect(Komponents_all$ID_Komponente,"^K2ST2-")]$ID_Komponente <- "K2ST2"
Komponents_all[str_detect(Komponents_all$ID_Komponente,"^K2ST1")]$ID_Komponente <- "K2ST1"
Komponents_all[str_detect(Komponents_all$ID_Komponente,"^K2LE2-")]$ID_Komponente <- "K2LE2"
Komponents_all[str_detect(Komponents_all$ID_Komponente,"^K2LE1-")]$ID_Komponente <- "K2LE1"
Komponents_all[str_detect(Komponents_all$ID_Komponente,"^K1DI2-")]$ID_Komponente <- "K1DI2"
Komponents_all[str_detect(Komponents_all$ID_Komponente,"^K1DI1-")]$ID_Komponente <- "K1DI1"
Komponents_all[str_detect(Komponents_all$ID_Komponente,"^K1BE2-")]$ID_Komponente <- "K1BE2"
Komponents_all[str_detect(Komponents_all$ID_Komponente,"^K1BE1-")]$ID_Komponente <- "K1BE1"


Komponents_all_Month<-Komponents_all
Komponents_all_Month$Produktionsdatum <- format(as.Date(Komponents_all_Month$Produktionsdatum, format="%Y-%m-%d"),"%Y-%m")

Komponents_all$Produktionsdatum <- format(as.Date(Komponents_all$Produktionsdatum, format="%Y-%m-%d"),"%Y")

#Summarizing Data

Y2008 <- filter(Komponents_all,Produktionsdatum == "2008") %>% group_by(ID_Komponente,Werksnummer)%>% summarise(Defect=sum(Fehlerhaft))

Y2008 <- Y2008[order(Y2008$Defect,decreasing = TRUE),]

Y2009 <- filter(Komponents_all,Produktionsdatum == "2009") %>% group_by(ID_Komponente,Werksnummer)%>% summarise(Defect=sum(Fehlerhaft))

Y2009 <- Y2009[order(Y2009$Defect,decreasing = TRUE),]

Y2010 <- filter(Komponents_all,Produktionsdatum == "2010") %>% group_by(ID_Komponente,Werksnummer)%>% summarise(Defect=sum(Fehlerhaft))

Y2010 <- Y2010[order(Y2010$Defect,decreasing = TRUE),]

Y2011 <- filter(Komponents_all,Produktionsdatum == "2011") %>% group_by(ID_Komponente,Werksnummer)%>% summarise(Defect=sum(Fehlerhaft))

Y2011 <- Y2011[order(Y2011$Defect,decreasing = TRUE),]

Y2012 <- filter(Komponents_all,Produktionsdatum == "2012") %>% group_by(ID_Komponente,Werksnummer)%>% summarise(Defect=sum(Fehlerhaft))

Y2012 <- Y2012[order(Y2012$Defect,decreasing = TRUE),]

Y2013 <- filter(Komponents_all,Produktionsdatum == "2013") %>% group_by(ID_Komponente,Werksnummer)%>% summarise(Defect=sum(Fehlerhaft))

Y2013 <- Y2013[order(Y2013$Defect,decreasing = TRUE),]

Y2014 <- filter(Komponents_all,Produktionsdatum == "2014") %>% group_by(ID_Komponente,Werksnummer)%>% summarise(Defect=sum(Fehlerhaft))

Y2014 <- Y2014[order(Y2014$Defect,decreasing = TRUE),]

Y2015 <- filter(Komponents_all,Produktionsdatum == "2015") %>% group_by(ID_Komponente,Werksnummer)%>% summarise(Defect=sum(Fehlerhaft))

Y2015 <- Y2015[order(Y2015$Defect,decreasing = TRUE),]

Y2016 <- filter(Komponents_all,Produktionsdatum == "2016") %>% group_by(ID_Komponente,Werksnummer)%>% summarise(Defect=sum(Fehlerhaft))

Y2016 <- Y2016[order(Y2016$Defect,decreasing = TRUE),]

#2008

Y2008_K4 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2008")] %>% filter(ID_Komponente == "K4")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2008_K4$Werksnummer <- factor(Y2008_K4$Werksnummer)

Y2008_K2ST1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2008")] %>% filter(ID_Komponente == "K2ST1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2008_K2ST1$Werksnummer <- factor(Y2008_K2ST1$Werksnummer)

Y2008_K1BE1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2008")] %>% filter(ID_Komponente == "K1BE1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2008_K1BE1$Werksnummer <- factor(Y2008_K1BE1$Werksnummer)

Y2008_K3SG1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2008")] %>% filter(ID_Komponente == "K3SG1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2008_K3SG1$Werksnummer <- factor(Y2008_K3SG1$Werksnummer)

Y2008_K2ST2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2008")] %>% filter(ID_Komponente == "K2ST2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2008_K2ST2$Werksnummer <- factor(Y2008_K2ST2$Werksnummer)

Y2008_K1BE2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2008")] %>% filter(ID_Komponente == "K1BE2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2008_K1BE2$Werksnummer <- factor(Y2008_K1BE2$Werksnummer)

Y2008_K1DI1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2008")] %>% filter(ID_Komponente == "K1DI1") %>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2008_K1DI1$Werksnummer <- factor(Y2008_K1DI1$Werksnummer)

Y2008_K6 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2008")] %>% filter(ID_Komponente == "K6")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2008_K6$Werksnummer <- factor(Y2008_K6$Werksnummer)

Y2008_K2LE1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2008")] %>% filter(ID_Komponente == "K2LE1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2008_K2LE1$Werksnummer <- factor(Y2008_K2LE1$Werksnummer)

Y2008_K5 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2008")] %>% filter(ID_Komponente == "K5")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2008_K5$Werksnummer <- factor(Y2008_K5$Werksnummer)

Y2008_K2LE2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2008")] %>% filter(ID_Komponente == "K2LE2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2008_K2LE2$Werksnummer <- factor(Y2008_K2LE2$Werksnummer)

Y2008_K7 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2008")] %>% filter(ID_Komponente == "K7")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2008_K7$Werksnummer <- factor(Y2008_K7$Werksnummer)

Y2008_K3SG2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2008")] %>% filter(ID_Komponente == "K3SG2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2008_K3SG2$Werksnummer <- factor(Y2008_K3SG2$Werksnummer)

Y2008_K3AG1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2008")] %>% filter(ID_Komponente == "K3AG1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2008_K3AG1$Werksnummer <- factor(Y2008_K3AG1$Werksnummer)

Y2008_K1DI2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2008")] %>% filter(ID_Komponente == "K1DI2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2008_K1DI2$Werksnummer <- factor(Y2008_K1DI2$Werksnummer)

Y2008_K3AG2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2008")] %>% filter(ID_Komponente == "K3AG2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2008_K3AG2$Werksnummer <- factor(Y2008_K3AG2$Werksnummer)


#2009

Y2009_K4 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2009")] %>% filter(ID_Komponente == "K4")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2009_K4$Werksnummer <- factor(Y2009_K4$Werksnummer)

Y2009_K2ST1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2009")] %>% filter(ID_Komponente == "K2ST1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2009_K2ST1$Werksnummer <- factor(Y2009_K2ST1$Werksnummer)

Y2009_K1BE1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2009")] %>% filter(ID_Komponente == "K1BE1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2009_K1BE1$Werksnummer <- factor(Y2009_K1BE1$Werksnummer)

Y2009_K3SG1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2009")] %>% filter(ID_Komponente == "K3SG1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2009_K3SG1$Werksnummer <- factor(Y2009_K3SG1$Werksnummer)

Y2009_K2ST2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2009")] %>% filter(ID_Komponente == "K2ST2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2009_K2ST2$Werksnummer <- factor(Y2009_K2ST2$Werksnummer)

Y2009_K1BE2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2009")] %>% filter(ID_Komponente == "K1BE2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2009_K1BE2$Werksnummer <- factor(Y2009_K1BE2$Werksnummer)

Y2009_K1DI1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2009")] %>% filter(ID_Komponente == "K1DI1") %>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2009_K1DI1$Werksnummer <- factor(Y2009_K1DI1$Werksnummer)

Y2009_K6 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2009")] %>% filter(ID_Komponente == "K6")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2009_K6$Werksnummer <- factor(Y2009_K6$Werksnummer)

Y2009_K2LE1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2009")] %>% filter(ID_Komponente == "K2LE1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2009_K2LE1$Werksnummer <- factor(Y2009_K2LE1$Werksnummer)

Y2009_K5 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2009")] %>% filter(ID_Komponente == "K5")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2009_K5$Werksnummer <- factor(Y2009_K5$Werksnummer)

Y2009_K2LE2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2009")] %>% filter(ID_Komponente == "K2LE2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2009_K2LE2$Werksnummer <- factor(Y2009_K2LE2$Werksnummer)

Y2009_K7 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2009")] %>% filter(ID_Komponente == "K7")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2009_K7$Werksnummer <- factor(Y2009_K7$Werksnummer)

Y2009_K3SG2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2009")] %>% filter(ID_Komponente == "K3SG2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2009_K3SG2$Werksnummer <- factor(Y2009_K3SG2$Werksnummer)

Y2009_K3AG1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2009")] %>% filter(ID_Komponente == "K3AG1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))

Y2009_K3AG1$Werksnummer <- factor(Y2009_K3AG1$Werksnummer)

Y2009_K1DI2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2009")] %>% filter(ID_Komponente == "K1DI2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2009_K1DI2$Werksnummer <- factor(Y2009_K1DI2$Werksnummer)
Y2009_K3AG2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2009")] %>% filter(ID_Komponente == "K3AG2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2009_K3AG2$Werksnummer <- factor(Y2009_K3AG2$Werksnummer)
#2010
Y2010_K4 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2010")] %>% filter(ID_Komponente == "K4")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2010_K4$Werksnummer <- factor(Y2010_K4$Werksnummer)
Y2010_K2ST1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2010")] %>% filter(ID_Komponente == "K2ST1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2010_K2ST1$Werksnummer <- factor(Y2010_K2ST1$Werksnummer)
Y2010_K1BE1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2010")] %>% filter(ID_Komponente == "K1BE1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2010_K1BE1$Werksnummer <- factor(Y2010_K1BE1$Werksnummer)
Y2010_K3SG1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2010")] %>% filter(ID_Komponente == "K3SG1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2010_K3SG1$Werksnummer <- factor(Y2010_K3SG1$Werksnummer)
Y2010_K2ST2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2010")] %>% filter(ID_Komponente == "K2ST2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2010_K2ST2$Werksnummer <- factor(Y2010_K2ST2$Werksnummer)
Y2010_K1BE2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2010")] %>% filter(ID_Komponente == "K1BE2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2010_K1BE2$Werksnummer <- factor(Y2010_K1BE2$Werksnummer)
Y2010_K1DI1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2010")] %>% filter(ID_Komponente == "K1DI1") %>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2010_K1DI1$Werksnummer <- factor(Y2010_K1DI1$Werksnummer)
Y2010_K6 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2010")] %>% filter(ID_Komponente == "K6")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2010_K6$Werksnummer <- factor(Y2010_K6$Werksnummer)
Y2010_K2LE1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2010")] %>% filter(ID_Komponente == "K2LE1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2010_K2LE1$Werksnummer <- factor(Y2010_K2LE1$Werksnummer)
Y2010_K5 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2010")] %>% filter(ID_Komponente == "K5")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2010_K5$Werksnummer <- factor(Y2010_K5$Werksnummer)
Y2010_K2LE2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2010")] %>% filter(ID_Komponente == "K2LE2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2010_K2LE2$Werksnummer <- factor(Y2010_K2LE2$Werksnummer)
Y2010_K7 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2010")] %>% filter(ID_Komponente == "K7")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2010_K7$Werksnummer <- factor(Y2010_K7$Werksnummer)
Y2010_K3SG2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2010")] %>% filter(ID_Komponente == "K3SG2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2010_K3SG2$Werksnummer <- factor(Y2010_K3SG2$Werksnummer)
Y2010_K3AG1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2010")] %>% filter(ID_Komponente == "K3AG1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2010_K3AG1$Werksnummer <- factor(Y2010_K3AG1$Werksnummer)
Y2010_K1DI2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2010")] %>% filter(ID_Komponente == "K1DI2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2010_K1DI2$Werksnummer <- factor(Y2010_K1DI2$Werksnummer)
Y2010_K3AG2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2010")] %>% filter(ID_Komponente == "K3AG2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2010_K3AG2$Werksnummer <- factor(Y2010_K3AG2$Werksnummer)
#2011
Y2011_K4 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2011")] %>% filter(ID_Komponente == "K4")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2011_K4$Werksnummer <- factor(Y2011_K4$Werksnummer)
Y2011_K2ST1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2011")] %>% filter(ID_Komponente == "K2ST1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2011_K2ST1$Werksnummer <- factor(Y2011_K2ST1$Werksnummer)
Y2011_K1BE1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2011")] %>% filter(ID_Komponente == "K1BE1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2011_K1BE1$Werksnummer <- factor(Y2011_K1BE1$Werksnummer)
Y2011_K3SG1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2011")] %>% filter(ID_Komponente == "K3SG1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2011_K3SG1$Werksnummer <- factor(Y2011_K3SG1$Werksnummer)
Y2011_K2ST2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2011")] %>% filter(ID_Komponente == "K2ST2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2011_K2ST2$Werksnummer <- factor(Y2011_K2ST2$Werksnummer)
Y2011_K1BE2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2011")] %>% filter(ID_Komponente == "K1BE2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2011_K1BE2$Werksnummer <- factor(Y2011_K1BE2$Werksnummer)
Y2011_K1DI1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2011")] %>% filter(ID_Komponente == "K1DI1") %>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2011_K1DI1$Werksnummer <- factor(Y2011_K1DI1$Werksnummer)
Y2011_K6 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2011")] %>% filter(ID_Komponente == "K6")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2011_K6$Werksnummer <- factor(Y2011_K6$Werksnummer)
Y2011_K2LE1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2011")] %>% filter(ID_Komponente == "K2LE1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2011_K2LE1$Werksnummer <- factor(Y2011_K2LE1$Werksnummer)
Y2011_K5 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2011")] %>% filter(ID_Komponente == "K5")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2011_K5$Werksnummer <- factor(Y2011_K5$Werksnummer)
Y2011_K2LE2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2011")] %>% filter(ID_Komponente == "K2LE2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2011_K2LE2$Werksnummer <- factor(Y2011_K2LE2$Werksnummer)
Y2011_K7 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2011")] %>% filter(ID_Komponente == "K7")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2011_K7$Werksnummer <- factor(Y2011_K7$Werksnummer)
Y2011_K3SG2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2011")] %>% filter(ID_Komponente == "K3SG2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2011_K3SG2$Werksnummer <- factor(Y2011_K3SG2$Werksnummer)
Y2011_K3AG1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2011")] %>% filter(ID_Komponente == "K3AG1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2011_K3AG1$Werksnummer <- factor(Y2011_K3AG1$Werksnummer)
Y2011_K1DI2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2011")] %>% filter(ID_Komponente == "K1DI2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2011_K1DI2$Werksnummer <- factor(Y2011_K1DI2$Werksnummer)
Y2011_K3AG2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2011")] %>% filter(ID_Komponente == "K3AG2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2011_K3AG2$Werksnummer <- factor(Y2011_K3AG2$Werksnummer)
#2012
Y2012_K4 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2012")] %>% filter(ID_Komponente == "K4")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2012_K4$Werksnummer <- factor(Y2012_K4$Werksnummer)
Y2012_K2ST1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2012")] %>% filter(ID_Komponente == "K2ST1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2012_K2ST1$Werksnummer <- factor(Y2012_K2ST1$Werksnummer)
Y2012_K1BE1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2012")] %>% filter(ID_Komponente == "K1BE1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2012_K1BE1$Werksnummer <- factor(Y2012_K1BE1$Werksnummer)
Y2012_K3SG1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2012")] %>% filter(ID_Komponente == "K3SG1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2012_K3SG1$Werksnummer <- factor(Y2012_K3SG1$Werksnummer)
Y2012_K2ST2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2012")] %>% filter(ID_Komponente == "K2ST2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2012_K2ST2$Werksnummer <- factor(Y2012_K2ST2$Werksnummer)
Y2012_K1BE2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2012")] %>% filter(ID_Komponente == "K1BE2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2012_K1BE2$Werksnummer <- factor(Y2012_K1BE2$Werksnummer)
Y2012_K1DI1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2012")] %>% filter(ID_Komponente == "K1DI1") %>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2012_K1DI1$Werksnummer <- factor(Y2012_K1DI1$Werksnummer)
Y2012_K6 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2012")] %>% filter(ID_Komponente == "K6")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2012_K6$Werksnummer <- factor(Y2012_K6$Werksnummer)
Y2012_K2LE1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2012")] %>% filter(ID_Komponente == "K2LE1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2012_K2LE1$Werksnummer <- factor(Y2012_K2LE1$Werksnummer)
Y2012_K5 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2012")] %>% filter(ID_Komponente == "K5")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2012_K5$Werksnummer <- factor(Y2012_K5$Werksnummer)
Y2012_K2LE2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2012")] %>% filter(ID_Komponente == "K2LE2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2012_K2LE2$Werksnummer <- factor(Y2012_K2LE2$Werksnummer)
Y2012_K7 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2012")] %>% filter(ID_Komponente == "K7")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2012_K7$Werksnummer <- factor(Y2012_K7$Werksnummer)
Y2012_K3SG2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2012")] %>% filter(ID_Komponente == "K3SG2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2012_K3SG2$Werksnummer <- factor(Y2012_K3SG2$Werksnummer)
Y2012_K3AG1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2012")] %>% filter(ID_Komponente == "K3AG1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2012_K3AG1$Werksnummer <- factor(Y2012_K3AG1$Werksnummer)
Y2012_K1DI2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2012")] %>% filter(ID_Komponente == "K1DI2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2012_K1DI2$Werksnummer <- factor(Y2012_K1DI2$Werksnummer)
Y2012_K3AG2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2012")] %>% filter(ID_Komponente == "K3AG2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2012_K3AG2$Werksnummer <- factor(Y2012_K3AG2$Werksnummer)
#2013
Y2013_K4 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2013")] %>% filter(ID_Komponente == "K4")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2013_K4$Werksnummer <- factor(Y2013_K4$Werksnummer)
Y2013_K2ST1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2013")] %>% filter(ID_Komponente == "K2ST1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2013_K2ST1$Werksnummer <- factor(Y2013_K2ST1$Werksnummer)
Y2013_K1BE1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2013")] %>% filter(ID_Komponente == "K1BE1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2013_K1BE1$Werksnummer <- factor(Y2013_K1BE1$Werksnummer)
Y2013_K3SG1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2013")] %>% filter(ID_Komponente == "K3SG1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2013_K3SG1$Werksnummer <- factor(Y2013_K3SG1$Werksnummer)
Y2013_K2ST2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2013")] %>% filter(ID_Komponente == "K2ST2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2013_K2ST2$Werksnummer <- factor(Y2013_K2ST2$Werksnummer)
Y2013_K1BE2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2013")] %>% filter(ID_Komponente == "K1BE2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2013_K1BE2$Werksnummer <- factor(Y2013_K1BE2$Werksnummer)
Y2013_K1DI1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2013")] %>% filter(ID_Komponente == "K1DI1") %>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2013_K1DI1$Werksnummer <- factor(Y2013_K1DI1$Werksnummer)
Y2013_K6 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2013")] %>% filter(ID_Komponente == "K6")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2013_K6$Werksnummer <- factor(Y2013_K6$Werksnummer)
Y2013_K2LE1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2013")] %>% filter(ID_Komponente == "K2LE1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2013_K2LE1$Werksnummer <- factor(Y2013_K2LE1$Werksnummer)
Y2013_K5 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2013")] %>% filter(ID_Komponente == "K5")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2013_K5$Werksnummer <- factor(Y2013_K5$Werksnummer)
Y2013_K2LE2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2013")] %>% filter(ID_Komponente == "K2LE2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2013_K2LE2$Werksnummer <- factor(Y2013_K2LE2$Werksnummer)
Y2013_K7 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2013")] %>% filter(ID_Komponente == "K7")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2013_K7$Werksnummer <- factor(Y2013_K7$Werksnummer)
Y2013_K3SG2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2013")] %>% filter(ID_Komponente == "K3SG2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2013_K3SG2$Werksnummer <- factor(Y2013_K3SG2$Werksnummer)
Y2013_K3AG1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2013")] %>% filter(ID_Komponente == "K3AG1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2013_K3AG1$Werksnummer <- factor(Y2013_K3AG1$Werksnummer)
Y2013_K1DI2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2013")] %>% filter(ID_Komponente == "K1DI2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2013_K1DI2$Werksnummer <- factor(Y2013_K1DI2$Werksnummer)
Y2013_K3AG2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2013")] %>% filter(ID_Komponente == "K3AG2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2013_K3AG2$Werksnummer <- factor(Y2013_K3AG2$Werksnummer)
#2014
Y2014_K4 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2014")] %>% filter(ID_Komponente == "K4")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2014_K4$Werksnummer <- factor(Y2014_K4$Werksnummer)
Y2014_K2ST1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2014")] %>% filter(ID_Komponente == "K2ST1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2014_K2ST1$Werksnummer <- factor(Y2014_K2ST1$Werksnummer)
Y2014_K1BE1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2014")] %>% filter(ID_Komponente == "K1BE1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2014_K1BE1$Werksnummer <- factor(Y2014_K1BE1$Werksnummer)
Y2014_K3SG1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2014")] %>% filter(ID_Komponente == "K3SG1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2014_K3SG1$Werksnummer <- factor(Y2014_K3SG1$Werksnummer)
Y2014_K2ST2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2014")] %>% filter(ID_Komponente == "K2ST2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2014_K2ST2$Werksnummer <- factor(Y2014_K2ST2$Werksnummer)
Y2014_K1BE2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2014")] %>% filter(ID_Komponente == "K1BE2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2014_K1BE2$Werksnummer <- factor(Y2014_K1BE2$Werksnummer)
Y2014_K1DI1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2014")] %>% filter(ID_Komponente == "K1DI1") %>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2014_K1DI1$Werksnummer <- factor(Y2014_K1DI1$Werksnummer)
Y2014_K6 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2014")] %>% filter(ID_Komponente == "K6")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2014_K6$Werksnummer <- factor(Y2014_K6$Werksnummer)
Y2014_K2LE1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2014")] %>% filter(ID_Komponente == "K2LE1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2014_K2LE1$Werksnummer <- factor(Y2014_K2LE1$Werksnummer)
Y2014_K5 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2014")] %>% filter(ID_Komponente == "K5")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2014_K5$Werksnummer <- factor(Y2014_K5$Werksnummer)
Y2014_K2LE2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2014")] %>% filter(ID_Komponente == "K2LE2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2014_K2LE2$Werksnummer <- factor(Y2014_K2LE2$Werksnummer)
Y2014_K7 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2014")] %>% filter(ID_Komponente == "K7")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2014_K7$Werksnummer <- factor(Y2014_K7$Werksnummer)
Y2014_K3SG2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2014")] %>% filter(ID_Komponente == "K3SG2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2014_K3SG2$Werksnummer <- factor(Y2014_K3SG2$Werksnummer)
Y2014_K3AG1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2014")] %>% filter(ID_Komponente == "K3AG1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2014_K3AG1$Werksnummer <- factor(Y2014_K3AG1$Werksnummer)
Y2014_K1DI2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2014")] %>% filter(ID_Komponente == "K1DI2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2014_K1DI2$Werksnummer <- factor(Y2014_K1DI2$Werksnummer)
Y2014_K3AG2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2014")] %>% filter(ID_Komponente == "K3AG2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2014_K3AG2$Werksnummer <- factor(Y2014_K3AG2$Werksnummer)
#2015
Y2015_K4 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2015")] %>% filter(ID_Komponente == "K4")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2015_K4$Werksnummer <- factor(Y2015_K4$Werksnummer)
Y2015_K2ST1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2015")] %>% filter(ID_Komponente == "K2ST1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2015_K2ST1$Werksnummer <- factor(Y2015_K2ST1$Werksnummer)
Y2015_K1BE1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2015")] %>% filter(ID_Komponente == "K1BE1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2015_K1BE1$Werksnummer <- factor(Y2015_K1BE1$Werksnummer)
Y2015_K3SG1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2015")] %>% filter(ID_Komponente == "K3SG1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2015_K3SG1$Werksnummer <- factor(Y2015_K3SG1$Werksnummer)
Y2015_K2ST2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2015")] %>% filter(ID_Komponente == "K2ST2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2015_K2ST2$Werksnummer <- factor(Y2015_K2ST2$Werksnummer)
Y2015_K1BE2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2015")] %>% filter(ID_Komponente == "K1BE2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2015_K1BE2$Werksnummer <- factor(Y2015_K1BE2$Werksnummer)
Y2015_K1DI1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2015")] %>% filter(ID_Komponente == "K1DI1") %>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2015_K1DI1$Werksnummer <- factor(Y2015_K1DI1$Werksnummer)
Y2015_K6 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2015")] %>% filter(ID_Komponente == "K6")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2015_K6$Werksnummer <- factor(Y2015_K6$Werksnummer)
Y2015_K2LE1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2015")] %>% filter(ID_Komponente == "K2LE1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2015_K2LE1$Werksnummer <- factor(Y2015_K2LE1$Werksnummer)
Y2015_K5 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2015")] %>% filter(ID_Komponente == "K5")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2015_K5$Werksnummer <- factor(Y2015_K5$Werksnummer)
Y2015_K2LE2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2015")] %>% filter(ID_Komponente == "K2LE2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2015_K2LE2$Werksnummer <- factor(Y2015_K2LE2$Werksnummer)
Y2015_K7 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2015")] %>% filter(ID_Komponente == "K7")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2015_K7$Werksnummer <- factor(Y2015_K7$Werksnummer)
Y2015_K3SG2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2015")] %>% filter(ID_Komponente == "K3SG2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2015_K3SG2$Werksnummer <- factor(Y2015_K3SG2$Werksnummer)
Y2015_K3AG1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2015")] %>% filter(ID_Komponente == "K3AG1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2015_K3AG1$Werksnummer <- factor(Y2015_K3AG1$Werksnummer)
Y2015_K1DI2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2015")] %>% filter(ID_Komponente == "K1DI2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2015_K1DI2$Werksnummer <- factor(Y2015_K1DI2$Werksnummer)
Y2015_K3AG2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2015")] %>% filter(ID_Komponente == "K3AG2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2015_K3AG2$Werksnummer <- factor(Y2015_K3AG2$Werksnummer)
#2016
Y2016_K4 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2016")] %>% filter(ID_Komponente == "K4")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2016_K4$Werksnummer <- factor(Y2016_K4$Werksnummer)
Y2016_K2ST1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2016")] %>% filter(ID_Komponente == "K2ST1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2016_K2ST1$Werksnummer <- factor(Y2016_K2ST1$Werksnummer)
Y2016_K1BE1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2016")] %>% filter(ID_Komponente == "K1BE1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2016_K1BE1$Werksnummer <- factor(Y2016_K1BE1$Werksnummer)
Y2016_K3SG1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2016")] %>% filter(ID_Komponente == "K3SG1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2016_K3SG1$Werksnummer <- factor(Y2016_K3SG1$Werksnummer)
Y2016_K2ST2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2016")] %>% filter(ID_Komponente == "K2ST2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2016_K2ST2$Werksnummer <- factor(Y2016_K2ST2$Werksnummer)
Y2016_K1BE2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2016")] %>% filter(ID_Komponente == "K1BE2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2016_K1BE2$Werksnummer <- factor(Y2016_K1BE2$Werksnummer)
Y2016_K1DI1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2016")] %>% filter(ID_Komponente == "K1DI1") %>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2016_K1DI1$Werksnummer <- factor(Y2016_K1DI1$Werksnummer)
Y2016_K6 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2016")] %>% filter(ID_Komponente == "K6")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2016_K6$Werksnummer <- factor(Y2016_K6$Werksnummer)
Y2016_K2LE1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2016")] %>% filter(ID_Komponente == "K2LE1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2016_K2LE1$Werksnummer <- factor(Y2016_K2LE1$Werksnummer)
Y2016_K5 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2016")] %>% filter(ID_Komponente == "K5")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2016_K5$Werksnummer <- factor(Y2016_K5$Werksnummer)
Y2016_K2LE2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2016")] %>% filter(ID_Komponente == "K2LE2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2016_K2LE2$Werksnummer <- factor(Y2016_K2LE2$Werksnummer)
Y2016_K7 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2016")] %>% filter(ID_Komponente == "K7")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2016_K7$Werksnummer <- factor(Y2016_K7$Werksnummer)
Y2016_K3SG2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2016")] %>% filter(ID_Komponente == "K3SG2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2016_K3SG2$Werksnummer <- factor(Y2016_K3SG2$Werksnummer)
Y2016_K3AG1 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2016")] %>% filter(ID_Komponente == "K3AG1")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2016_K3AG1$Werksnummer <- factor(Y2016_K3AG1$Werksnummer)
Y2016_K1DI2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2016")] %>% filter(ID_Komponente == "K1DI2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft))
Y2016_K1DI2$Werksnummer <- factor(Y2016_K1DI2$Werksnummer)
Y2016_K3AG2 <- Komponents_all_Month[str_detect(Komponents_all_Month$Produktionsdatum,"^2016")] %>% filter(ID_Komponente == "K3AG2")%>% group_by(Werksnummer,Produktionsdatum)%>% summarise(Defect=sum(Fehlerhaft)) 
Y2016_K3AG2$Werksnummer <- factor(Y2016_K3AG2$Werksnummer)
#2008
Y2008_K4_Cumulative <- Y2008_K4  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2008_K4 <- merge(x = Y2008_K4, y = Y2008_K4_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2008_K4_Cumulative)
Y2008_K2ST1_Cumulative<- Y2008_K2ST1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2008_K2ST1<- merge(x = Y2008_K2ST1, y = Y2008_K2ST1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2008_K2ST1_Cumulative)
Y2008_K1BE1_Cumulative<- Y2008_K1BE1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2008_K1BE1<- merge(x = Y2008_K1BE1, y = Y2008_K1BE1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2008_K1BE1_Cumulative)
Y2008_K3SG1_Cumulative<- Y2008_K3SG1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2008_K3SG1<- merge(x = Y2008_K3SG1, y = Y2008_K3SG1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2008_K3SG1_Cumulative)
Y2008_K2ST2_Cumulative<- Y2008_K2ST2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2008_K2ST2<- merge(x = Y2008_K2ST2, y = Y2008_K2ST2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2008_K2ST2_Cumulative)
Y2008_K1BE2_Cumulative<- Y2008_K1BE2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2008_K1BE2<- merge(x = Y2008_K1BE2, y = Y2008_K1BE2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2008_K1BE2_Cumulative)
Y2008_K1DI1_Cumulative<- Y2008_K1DI1 %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2008_K1DI1<- merge(x = Y2008_K1DI1, y = Y2008_K1DI1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2008_K1DI1_Cumulative)
Y2008_K6_Cumulative<- Y2008_K6  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2008_K6<- merge(x = Y2008_K6, y = Y2008_K6_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2008_K6_Cumulative)
Y2008_K2LE1_Cumulative<- Y2008_K2LE1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2008_K2LE1<- merge(x = Y2008_K2LE1, y = Y2008_K2LE1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2008_K2LE1_Cumulative)
Y2008_K5_Cumulative<- Y2008_K5  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2008_K5<- merge(x = Y2008_K5, y = Y2008_K5_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2008_K5_Cumulative)
Y2008_K2LE2_Cumulative<- Y2008_K2LE2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2008_K2LE2<- merge(x = Y2008_K2LE2, y = Y2008_K2LE2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2008_K2LE2_Cumulative)
Y2008_K7_Cumulative<- Y2008_K7  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2008_K7<- merge(x = Y2008_K7, y = Y2008_K7_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2008_K7_Cumulative)
Y2008_K3SG2_Cumulative<- Y2008_K3SG2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2008_K3SG2<- merge(x = Y2008_K3SG2, y = Y2008_K3SG2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2008_K3SG2_Cumulative)
Y2008_K3AG1_Cumulative<- Y2008_K3AG1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2008_K3AG1<- merge(x = Y2008_K3AG1, y = Y2008_K3AG1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2008_K3AG1_Cumulative)
Y2008_K1DI2_Cumulative<- Y2008_K1DI2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2008_K1DI2<- merge(x = Y2008_K1DI2, y = Y2008_K1DI2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2008_K1DI2_Cumulative)
Y2008_K3AG2_Cumulative<- Y2008_K3AG2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2008_K3AG2 <- merge(x = Y2008_K3AG2, y = Y2008_K3AG2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2008_K3AG2_Cumulative)
#2009
Y2009_K4_Cumulative <- Y2009_K4  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2009_K4 <- merge(x = Y2009_K4, y = Y2009_K4_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2009_K4_Cumulative)
Y2009_K2ST1_Cumulative<- Y2009_K2ST1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2009_K2ST1<- merge(x = Y2009_K2ST1, y = Y2009_K2ST1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2009_K2ST1_Cumulative)
Y2009_K1BE1_Cumulative<- Y2009_K1BE1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2009_K1BE1<- merge(x = Y2009_K1BE1, y = Y2009_K1BE1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2009_K1BE1_Cumulative)
Y2009_K3SG1_Cumulative<- Y2009_K3SG1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2009_K3SG1<- merge(x = Y2009_K3SG1, y = Y2009_K3SG1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2009_K3SG1_Cumulative)
Y2009_K2ST2_Cumulative<- Y2009_K2ST2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2009_K2ST2<- merge(x = Y2009_K2ST2, y = Y2009_K2ST2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2009_K2ST2_Cumulative)
Y2009_K1BE2_Cumulative<- Y2009_K1BE2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2009_K1BE2<- merge(x = Y2009_K1BE2, y = Y2009_K1BE2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2009_K1BE2_Cumulative)
Y2009_K1DI1_Cumulative<- Y2009_K1DI1 %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2009_K1DI1<- merge(x = Y2009_K1DI1, y = Y2009_K1DI1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2009_K1DI1_Cumulative)
Y2009_K6_Cumulative<- Y2009_K6  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2009_K6<- merge(x = Y2009_K6, y = Y2009_K6_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2009_K6_Cumulative)
Y2009_K2LE1_Cumulative<- Y2009_K2LE1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2009_K2LE1<- merge(x = Y2009_K2LE1, y = Y2009_K2LE1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2009_K2LE1_Cumulative)
Y2009_K5_Cumulative<- Y2009_K5  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2009_K5<- merge(x = Y2009_K5, y = Y2009_K5_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2009_K5_Cumulative)
Y2009_K2LE2_Cumulative<- Y2009_K2LE2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2009_K2LE2<- merge(x = Y2009_K2LE2, y = Y2009_K2LE2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2009_K2LE2_Cumulative)
Y2009_K7_Cumulative<- Y2009_K7  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2009_K7<- merge(x = Y2009_K7, y = Y2009_K7_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2009_K7_Cumulative)
Y2009_K3SG2_Cumulative<- Y2009_K3SG2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2009_K3SG2<- merge(x = Y2009_K3SG2, y = Y2009_K3SG2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2009_K3SG2_Cumulative)
Y2009_K3AG1_Cumulative<- Y2009_K3AG1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2009_K3AG1<- merge(x = Y2009_K3AG1, y = Y2009_K3AG1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2009_K3AG1_Cumulative)
Y2009_K1DI2_Cumulative<- Y2009_K1DI2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2009_K1DI2<- merge(x = Y2009_K1DI2, y = Y2009_K1DI2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2009_K1DI2_Cumulative)
Y2009_K3AG2_Cumulative<- Y2009_K3AG2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2009_K3AG2 <- merge(x = Y2009_K3AG2, y = Y2009_K3AG2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2009_K3AG2_Cumulative)
#2010
Y2010_K4_Cumulative <- Y2010_K4  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2010_K4 <- merge(x = Y2010_K4, y = Y2010_K4_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2010_K4_Cumulative)
Y2010_K2ST1_Cumulative<- Y2010_K2ST1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2010_K2ST1<- merge(x = Y2010_K2ST1, y = Y2010_K2ST1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2010_K2ST1_Cumulative)
Y2010_K1BE1_Cumulative<- Y2010_K1BE1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2010_K1BE1<- merge(x = Y2010_K1BE1, y = Y2010_K1BE1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2010_K1BE1_Cumulative)
Y2010_K3SG1_Cumulative<- Y2010_K3SG1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2010_K3SG1<- merge(x = Y2010_K3SG1, y = Y2010_K3SG1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2010_K3SG1_Cumulative)
Y2010_K2ST2_Cumulative<- Y2010_K2ST2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2010_K2ST2<- merge(x = Y2010_K2ST2, y = Y2010_K2ST2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2010_K2ST2_Cumulative)
Y2010_K1BE2_Cumulative<- Y2010_K1BE2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2010_K1BE2<- merge(x = Y2010_K1BE2, y = Y2010_K1BE2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2010_K1BE2_Cumulative)
Y2010_K1DI1_Cumulative<- Y2010_K1DI1 %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2010_K1DI1<- merge(x = Y2010_K1DI1, y = Y2010_K1DI1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2010_K1DI1_Cumulative)
Y2010_K6_Cumulative<- Y2010_K6  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2010_K6<- merge(x = Y2010_K6, y = Y2010_K6_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2010_K6_Cumulative)
Y2010_K2LE1_Cumulative<- Y2010_K2LE1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2010_K2LE1<- merge(x = Y2010_K2LE1, y = Y2010_K2LE1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2010_K2LE1_Cumulative)
Y2010_K5_Cumulative<- Y2010_K5  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2010_K5<- merge(x = Y2010_K5, y = Y2010_K5_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2010_K5_Cumulative)
Y2010_K2LE2_Cumulative<- Y2010_K2LE2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2010_K2LE2<- merge(x = Y2010_K2LE2, y = Y2010_K2LE2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2010_K2LE2_Cumulative)
Y2010_K7_Cumulative<- Y2010_K7  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2010_K7<- merge(x = Y2010_K7, y = Y2010_K7_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2010_K7_Cumulative)
Y2010_K3SG2_Cumulative<- Y2010_K3SG2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2010_K3SG2<- merge(x = Y2010_K3SG2, y = Y2010_K3SG2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2010_K3SG2_Cumulative)
Y2010_K3AG1_Cumulative<- Y2010_K3AG1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2010_K3AG1<- merge(x = Y2010_K3AG1, y = Y2010_K3AG1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2010_K3AG1_Cumulative)
Y2010_K1DI2_Cumulative<- Y2010_K1DI2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2010_K1DI2<- merge(x = Y2010_K1DI2, y = Y2010_K1DI2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2010_K1DI2_Cumulative)
Y2010_K3AG2_Cumulative<- Y2010_K3AG2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2010_K3AG2 <- merge(x = Y2010_K3AG2, y = Y2010_K3AG2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2010_K3AG2_Cumulative)
#2011
Y2011_K4_Cumulative <- Y2011_K4  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2011_K4 <- merge(x = Y2011_K4, y = Y2011_K4_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2011_K4_Cumulative)
Y2011_K2ST1_Cumulative<- Y2011_K2ST1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2011_K2ST1<- merge(x = Y2011_K2ST1, y = Y2011_K2ST1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2011_K2ST1_Cumulative)
Y2011_K1BE1_Cumulative<- Y2011_K1BE1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2011_K1BE1<- merge(x = Y2011_K1BE1, y = Y2011_K1BE1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2011_K1BE1_Cumulative)
Y2011_K3SG1_Cumulative<- Y2011_K3SG1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2011_K3SG1<- merge(x = Y2011_K3SG1, y = Y2011_K3SG1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2011_K3SG1_Cumulative)
Y2011_K2ST2_Cumulative<- Y2011_K2ST2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2011_K2ST2<- merge(x = Y2011_K2ST2, y = Y2011_K2ST2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2011_K2ST2_Cumulative)
Y2011_K1BE2_Cumulative<- Y2011_K1BE2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2011_K1BE2<- merge(x = Y2011_K1BE2, y = Y2011_K1BE2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2011_K1BE2_Cumulative)
Y2011_K1DI1_Cumulative<- Y2011_K1DI1 %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2011_K1DI1<- merge(x = Y2011_K1DI1, y = Y2011_K1DI1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2011_K1DI1_Cumulative)
Y2011_K6_Cumulative<- Y2011_K6  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2011_K6<- merge(x = Y2011_K6, y = Y2011_K6_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2011_K6_Cumulative)
Y2011_K2LE1_Cumulative<- Y2011_K2LE1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2011_K2LE1<- merge(x = Y2011_K2LE1, y = Y2011_K2LE1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2011_K2LE1_Cumulative)
Y2011_K5_Cumulative<- Y2011_K5  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2011_K5<- merge(x = Y2011_K5, y = Y2011_K5_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2011_K5_Cumulative)
Y2011_K2LE2_Cumulative<- Y2011_K2LE2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2011_K2LE2<- merge(x = Y2011_K2LE2, y = Y2011_K2LE2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2011_K2LE2_Cumulative)
Y2011_K7_Cumulative<- Y2011_K7  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2011_K7<- merge(x = Y2011_K7, y = Y2011_K7_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2011_K7_Cumulative)
Y2011_K3SG2_Cumulative<- Y2011_K3SG2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2011_K3SG2<- merge(x = Y2011_K3SG2, y = Y2011_K3SG2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2011_K3SG2_Cumulative)
Y2011_K3AG1_Cumulative<- Y2011_K3AG1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2011_K3AG1<- merge(x = Y2011_K3AG1, y = Y2011_K3AG1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2011_K3AG1_Cumulative)
Y2011_K1DI2_Cumulative<- Y2011_K1DI2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2011_K1DI2<- merge(x = Y2011_K1DI2, y = Y2011_K1DI2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2011_K1DI2_Cumulative)
Y2011_K3AG2_Cumulative<- Y2011_K3AG2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2011_K3AG2 <- merge(x = Y2011_K3AG2, y = Y2011_K3AG2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2011_K3AG2_Cumulative)
#2012
Y2012_K4_Cumulative <- Y2012_K4  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2012_K4 <- merge(x = Y2012_K4, y = Y2012_K4_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2012_K4_Cumulative)
Y2012_K2ST1_Cumulative<- Y2012_K2ST1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2012_K2ST1<- merge(x = Y2012_K2ST1, y = Y2012_K2ST1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2012_K2ST1_Cumulative)
Y2012_K1BE1_Cumulative<- Y2012_K1BE1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2012_K1BE1<- merge(x = Y2012_K1BE1, y = Y2012_K1BE1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2012_K1BE1_Cumulative)
Y2012_K3SG1_Cumulative<- Y2012_K3SG1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2012_K3SG1<- merge(x = Y2012_K3SG1, y = Y2012_K3SG1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2012_K3SG1_Cumulative)
Y2012_K2ST2_Cumulative<- Y2012_K2ST2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2012_K2ST2<- merge(x = Y2012_K2ST2, y = Y2012_K2ST2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2012_K2ST2_Cumulative)
Y2012_K1BE2_Cumulative<- Y2012_K1BE2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2012_K1BE2<- merge(x = Y2012_K1BE2, y = Y2012_K1BE2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2012_K1BE2_Cumulative)
Y2012_K1DI1_Cumulative<- Y2012_K1DI1 %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2012_K1DI1<- merge(x = Y2012_K1DI1, y = Y2012_K1DI1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2012_K1DI1_Cumulative)
Y2012_K6_Cumulative<- Y2012_K6  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2012_K6<- merge(x = Y2012_K6, y = Y2012_K6_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2012_K6_Cumulative)
Y2012_K2LE1_Cumulative<- Y2012_K2LE1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2012_K2LE1<- merge(x = Y2012_K2LE1, y = Y2012_K2LE1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2012_K2LE1_Cumulative)
Y2012_K5_Cumulative<- Y2012_K5  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2012_K5<- merge(x = Y2012_K5, y = Y2012_K5_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2012_K5_Cumulative)
Y2012_K2LE2_Cumulative<- Y2012_K2LE2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2012_K2LE2<- merge(x = Y2012_K2LE2, y = Y2012_K2LE2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2012_K2LE2_Cumulative)
Y2012_K7_Cumulative<- Y2012_K7  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2012_K7<- merge(x = Y2012_K7, y = Y2012_K7_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2012_K7_Cumulative)
Y2012_K3SG2_Cumulative<- Y2012_K3SG2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2012_K3SG2<- merge(x = Y2012_K3SG2, y = Y2012_K3SG2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2012_K3SG2_Cumulative)
Y2012_K3AG1_Cumulative<- Y2012_K3AG1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2012_K3AG1<- merge(x = Y2012_K3AG1, y = Y2012_K3AG1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2012_K3AG1_Cumulative)
Y2012_K1DI2_Cumulative<- Y2012_K1DI2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2012_K1DI2<- merge(x = Y2012_K1DI2, y = Y2012_K1DI2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2012_K1DI2_Cumulative)
Y2012_K3AG2_Cumulative<- Y2012_K3AG2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2012_K3AG2 <- merge(x = Y2012_K3AG2, y = Y2012_K3AG2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2012_K3AG2_Cumulative)
#2013
Y2013_K4_Cumulative <- Y2013_K4  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2013_K4 <- merge(x = Y2013_K4, y = Y2013_K4_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2013_K4_Cumulative)
Y2013_K2ST1_Cumulative<- Y2013_K2ST1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2013_K2ST1<- merge(x = Y2013_K2ST1, y = Y2013_K2ST1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2013_K2ST1_Cumulative)
Y2013_K1BE1_Cumulative<- Y2013_K1BE1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2013_K1BE1<- merge(x = Y2013_K1BE1, y = Y2013_K1BE1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2013_K1BE1_Cumulative)
Y2013_K3SG1_Cumulative<- Y2013_K3SG1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2013_K3SG1<- merge(x = Y2013_K3SG1, y = Y2013_K3SG1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2013_K3SG1_Cumulative)
Y2013_K2ST2_Cumulative<- Y2013_K2ST2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2013_K2ST2<- merge(x = Y2013_K2ST2, y = Y2013_K2ST2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2013_K2ST2_Cumulative)
Y2013_K1BE2_Cumulative<- Y2013_K1BE2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2013_K1BE2<- merge(x = Y2013_K1BE2, y = Y2013_K1BE2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2013_K1BE2_Cumulative)
Y2013_K1DI1_Cumulative<- Y2013_K1DI1 %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2013_K1DI1<- merge(x = Y2013_K1DI1, y = Y2013_K1DI1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2013_K1DI1_Cumulative)
Y2013_K6_Cumulative<- Y2013_K6  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2013_K6<- merge(x = Y2013_K6, y = Y2013_K6_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2013_K6_Cumulative)
Y2013_K2LE1_Cumulative<- Y2013_K2LE1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2013_K2LE1<- merge(x = Y2013_K2LE1, y = Y2013_K2LE1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2013_K2LE1_Cumulative)
Y2013_K5_Cumulative<- Y2013_K5  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2013_K5<- merge(x = Y2013_K5, y = Y2013_K5_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2013_K5_Cumulative)
Y2013_K2LE2_Cumulative<- Y2013_K2LE2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2013_K2LE2<- merge(x = Y2013_K2LE2, y = Y2013_K2LE2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2013_K2LE2_Cumulative)
Y2013_K7_Cumulative<- Y2013_K7  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2013_K7<- merge(x = Y2013_K7, y = Y2013_K7_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2013_K7_Cumulative)
Y2013_K3SG2_Cumulative<- Y2013_K3SG2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2013_K3SG2<- merge(x = Y2013_K3SG2, y = Y2013_K3SG2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2013_K3SG2_Cumulative)
Y2013_K3AG1_Cumulative<- Y2013_K3AG1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2013_K3AG1<- merge(x = Y2013_K3AG1, y = Y2013_K3AG1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2013_K3AG1_Cumulative)
Y2013_K1DI2_Cumulative<- Y2013_K1DI2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2013_K1DI2<- merge(x = Y2013_K1DI2, y = Y2013_K1DI2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2013_K1DI2_Cumulative)
Y2013_K3AG2_Cumulative<- Y2013_K3AG2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2013_K3AG2 <- merge(x = Y2013_K3AG2, y = Y2013_K3AG2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2013_K3AG2_Cumulative)
#2014
Y2014_K4_Cumulative <- Y2014_K4  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2014_K4 <- merge(x = Y2014_K4, y = Y2014_K4_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2014_K4_Cumulative)
Y2014_K2ST1_Cumulative<- Y2014_K2ST1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2014_K2ST1<- merge(x = Y2014_K2ST1, y = Y2014_K2ST1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2014_K2ST1_Cumulative)
Y2014_K1BE1_Cumulative<- Y2014_K1BE1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2014_K1BE1<- merge(x = Y2014_K1BE1, y = Y2014_K1BE1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2014_K1BE1_Cumulative)
Y2014_K3SG1_Cumulative<- Y2014_K3SG1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2014_K3SG1<- merge(x = Y2014_K3SG1, y = Y2014_K3SG1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2014_K3SG1_Cumulative)
Y2014_K2ST2_Cumulative<- Y2014_K2ST2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2014_K2ST2<- merge(x = Y2014_K2ST2, y = Y2014_K2ST2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2014_K2ST2_Cumulative)
Y2014_K1BE2_Cumulative<- Y2014_K1BE2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2014_K1BE2<- merge(x = Y2014_K1BE2, y = Y2014_K1BE2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2014_K1BE2_Cumulative)
Y2014_K1DI1_Cumulative<- Y2014_K1DI1 %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2014_K1DI1<- merge(x = Y2014_K1DI1, y = Y2014_K1DI1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2014_K1DI1_Cumulative)
Y2014_K6_Cumulative<- Y2014_K6  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2014_K6<- merge(x = Y2014_K6, y = Y2014_K6_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2014_K6_Cumulative)
Y2014_K2LE1_Cumulative<- Y2014_K2LE1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2014_K2LE1<- merge(x = Y2014_K2LE1, y = Y2014_K2LE1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2014_K2LE1_Cumulative)
Y2014_K5_Cumulative<- Y2014_K5  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2014_K5<- merge(x = Y2014_K5, y = Y2014_K5_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2014_K5_Cumulative)
Y2014_K2LE2_Cumulative<- Y2014_K2LE2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2014_K2LE2<- merge(x = Y2014_K2LE2, y = Y2014_K2LE2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2014_K2LE2_Cumulative)
Y2014_K7_Cumulative<- Y2014_K7  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2014_K7<- merge(x = Y2014_K7, y = Y2014_K7_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2014_K7_Cumulative)
Y2014_K3SG2_Cumulative<- Y2014_K3SG2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2014_K3SG2<- merge(x = Y2014_K3SG2, y = Y2014_K3SG2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2014_K3SG2_Cumulative)
Y2014_K3AG1_Cumulative<- Y2014_K3AG1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2014_K3AG1<- merge(x = Y2014_K3AG1, y = Y2014_K3AG1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2014_K3AG1_Cumulative)
Y2014_K1DI2_Cumulative<- Y2014_K1DI2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2014_K1DI2<- merge(x = Y2014_K1DI2, y = Y2014_K1DI2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2014_K1DI2_Cumulative)
Y2014_K3AG2_Cumulative<- Y2014_K3AG2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2014_K3AG2 <- merge(x = Y2014_K3AG2, y = Y2014_K3AG2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2014_K3AG2_Cumulative)
#2015
Y2015_K4_Cumulative <- Y2015_K4  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2015_K4 <- merge(x = Y2015_K4, y = Y2015_K4_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2015_K4_Cumulative)
Y2015_K2ST1_Cumulative<- Y2015_K2ST1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2015_K2ST1<- merge(x = Y2015_K2ST1, y = Y2015_K2ST1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2015_K2ST1_Cumulative)
Y2015_K1BE1_Cumulative<- Y2015_K1BE1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2015_K1BE1<- merge(x = Y2015_K1BE1, y = Y2015_K1BE1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2015_K1BE1_Cumulative)
Y2015_K3SG1_Cumulative<- Y2015_K3SG1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2015_K3SG1<- merge(x = Y2015_K3SG1, y = Y2015_K3SG1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2015_K3SG1_Cumulative)
Y2015_K2ST2_Cumulative<- Y2015_K2ST2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2015_K2ST2<- merge(x = Y2015_K2ST2, y = Y2015_K2ST2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2015_K2ST2_Cumulative)
Y2015_K1BE2_Cumulative<- Y2015_K1BE2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2015_K1BE2<- merge(x = Y2015_K1BE2, y = Y2015_K1BE2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2015_K1BE2_Cumulative)
Y2015_K1DI1_Cumulative<- Y2015_K1DI1 %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2015_K1DI1<- merge(x = Y2015_K1DI1, y = Y2015_K1DI1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2015_K1DI1_Cumulative)
Y2015_K6_Cumulative<- Y2015_K6  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2015_K6<- merge(x = Y2015_K6, y = Y2015_K6_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2015_K6_Cumulative)
Y2015_K2LE1_Cumulative<- Y2015_K2LE1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2015_K2LE1<- merge(x = Y2015_K2LE1, y = Y2015_K2LE1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2015_K2LE1_Cumulative)
Y2015_K5_Cumulative<- Y2015_K5  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2015_K5<- merge(x = Y2015_K5, y = Y2015_K5_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2015_K5_Cumulative)
Y2015_K2LE2_Cumulative<- Y2015_K2LE2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2015_K2LE2<- merge(x = Y2015_K2LE2, y = Y2015_K2LE2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2015_K2LE2_Cumulative)
Y2015_K7_Cumulative<- Y2015_K7  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2015_K7<- merge(x = Y2015_K7, y = Y2015_K7_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2015_K7_Cumulative)
Y2015_K3SG2_Cumulative<- Y2015_K3SG2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2015_K3SG2<- merge(x = Y2015_K3SG2, y = Y2015_K3SG2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2015_K3SG2_Cumulative)
Y2015_K3AG1_Cumulative<- Y2015_K3AG1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2015_K3AG1<- merge(x = Y2015_K3AG1, y = Y2015_K3AG1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2015_K3AG1_Cumulative)
Y2015_K1DI2_Cumulative<- Y2015_K1DI2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2015_K1DI2<- merge(x = Y2015_K1DI2, y = Y2015_K1DI2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2015_K1DI2_Cumulative)
Y2015_K3AG2_Cumulative<- Y2015_K3AG2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2015_K3AG2 <- merge(x = Y2015_K3AG2, y = Y2015_K3AG2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2015_K3AG2_Cumulative)
#2016
Y2016_K4_Cumulative <- Y2016_K4  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2016_K4 <- merge(x = Y2016_K4, y = Y2016_K4_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2016_K4_Cumulative)
Y2016_K2ST1_Cumulative<- Y2016_K2ST1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2016_K2ST1<- merge(x = Y2016_K2ST1, y = Y2016_K2ST1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2016_K2ST1_Cumulative)
Y2016_K1BE1_Cumulative<- Y2016_K1BE1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2016_K1BE1<- merge(x = Y2016_K1BE1, y = Y2016_K1BE1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2016_K1BE1_Cumulative)
Y2016_K3SG1_Cumulative<- Y2016_K3SG1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2016_K3SG1<- merge(x = Y2016_K3SG1, y = Y2016_K3SG1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2016_K3SG1_Cumulative)
Y2016_K2ST2_Cumulative<- Y2016_K2ST2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2016_K2ST2<- merge(x = Y2016_K2ST2, y = Y2016_K2ST2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2016_K2ST2_Cumulative)
Y2016_K1BE2_Cumulative<- Y2016_K1BE2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2016_K1BE2<- merge(x = Y2016_K1BE2, y = Y2016_K1BE2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2016_K1BE2_Cumulative)
Y2016_K1DI1_Cumulative<- Y2016_K1DI1 %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2016_K1DI1<- merge(x = Y2016_K1DI1, y = Y2016_K1DI1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2016_K1DI1_Cumulative)
Y2016_K6_Cumulative<- Y2016_K6  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2016_K6<- merge(x = Y2016_K6, y = Y2016_K6_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2016_K6_Cumulative)
Y2016_K2LE1_Cumulative<- Y2016_K2LE1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2016_K2LE1<- merge(x = Y2016_K2LE1, y = Y2016_K2LE1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2016_K2LE1_Cumulative)
Y2016_K5_Cumulative<- Y2016_K5  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2016_K5<- merge(x = Y2016_K5, y = Y2016_K5_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2016_K5_Cumulative)
Y2016_K2LE2_Cumulative<- Y2016_K2LE2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2016_K2LE2<- merge(x = Y2016_K2LE2, y = Y2016_K2LE2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2016_K2LE2_Cumulative)
Y2016_K7_Cumulative<- Y2016_K7  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2016_K7<- merge(x = Y2016_K7, y = Y2016_K7_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2016_K7_Cumulative)
Y2016_K3SG2_Cumulative<- Y2016_K3SG2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2016_K3SG2<- merge(x = Y2016_K3SG2, y = Y2016_K3SG2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2016_K3SG2_Cumulative)
Y2016_K3AG1_Cumulative<- Y2016_K3AG1  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2016_K3AG1<- merge(x = Y2016_K3AG1, y = Y2016_K3AG1_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2016_K3AG1_Cumulative)
Y2016_K1DI2_Cumulative<- Y2016_K1DI2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2016_K1DI2<- merge(x = Y2016_K1DI2, y = Y2016_K1DI2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2016_K1DI2_Cumulative)
Y2016_K3AG2_Cumulative<- Y2016_K3AG2  %>% group_by(Produktionsdatum) %>% summarise(cumulative=sum(Defect))
Y2016_K3AG2 <- merge(x = Y2016_K3AG2, y = Y2016_K3AG2_Cumulative, by = "Produktionsdatum", all.x = TRUE)
rm(Y2016_K3AG2_Cumulative)
rm(Komponents_all)
rm(Komponents_all_Month)
```

```{r Loading the Final Data Set, include=FALSE}
load("Final_Data_Group_14.RData", envir=.GlobalEnv)
```

```{r Combined Data for the Overall Defect Plot, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
Combined <- bind_rows(Y2008,Y2009,Y2010,Y2011,Y2012,Y2013,Y2014,Y2015,Y2016)
Combined$ID_Komponente  <- factor(Combined$ID_Komponente)
Combined$Werksnummer <- factor(Combined$Werksnummer)
```

```{r Polt for Overall Defects from 2008-2016, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

combinedplot <- ggplot(Combined,aes(x=Werksnummer,y=Defect,fill=ID_Komponente))+ geom_col() + labs(title="        Total Defects from 2008 to 2016 Across all Factories")
```

```{r Combined Plot, echo=FALSE, message=FALSE, warning=FALSE}

combinedplot

```
It could be seen from the Overall defect data for the time period from 2008 to 2016 that the Component with ID's "K2ST1" and "K2ST2" had a total of 190867 and 39294 defects respectively, which is 15.9% of the total defects of all the components in the time period. Therefore it would be logical to Conduct inspections in Factory -  <b> "1092" </b> which produces these components.

``` {r Pareto Charts 2008, eval=FALSE, include=FALSE}
Y2008_1011 <- ggplot(Y2008 %>% filter(Werksnummer==1011),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2008_1011")

Y2008_1021 <- ggplot(Y2008 %>% filter(Werksnummer==1021),aes(x=ID_Komponente,y=Defect)) + stat_pareto()+ labs(title="Y2008_1021")

Y2008_1031 <- ggplot(Y2008 %>% filter(Werksnummer==1031),aes(x=ID_Komponente,y=Defect)) + stat_pareto()+ labs(title="Y2008_1031")

Y2008_1041 <- ggplot(Y2008 %>% filter(Werksnummer==1041),aes(x=ID_Komponente,y=Defect)) + stat_pareto()+ labs(title="Y2008_1041")

Y2008_1051 <- ggplot(Y2008 %>% filter(Werksnummer==1051),aes(x=ID_Komponente,y=Defect)) + stat_pareto()+ labs(title="Y2008_1051")

Y2008_1061 <- ggplot(Y2008 %>% filter(Werksnummer==1061),aes(x=ID_Komponente,y=Defect)) + stat_pareto()+ labs(title="Y2008_1061")

Y2008_1071 <- ggplot(Y2008 %>% filter(Werksnummer==1071),aes(x=ID_Komponente,y=Defect)) + stat_pareto()+ labs(title="Y2008_1071")

Y2008_1072 <- ggplot(Y2008 %>% filter(Werksnummer==1072),aes(x=ID_Komponente,y=Defect)) + stat_pareto()+ labs(title="Y2008_1072")

Y2008_1081 <- ggplot(Y2008 %>% filter(Werksnummer==1081),aes(x=ID_Komponente,y=Defect)) + stat_pareto()+ labs(title="Y2008_1081")

Y2008_1082 <- ggplot(Y2008 %>% filter(Werksnummer==1082),aes(x=ID_Komponente,y=Defect)) + stat_pareto()+ labs(title="Y2008_1082")

Y2008_1091 <- ggplot(Y2008 %>% filter(Werksnummer==1091),aes(x=ID_Komponente,y=Defect)) + stat_pareto()+ labs(title="Y2008_1091")

Y2008_1092 <- ggplot(Y2008 %>% filter(Werksnummer==1092),aes(x=ID_Komponente,y=Defect)) + stat_pareto()+ labs(title="Y2008_1092")

Y2008_1111 <- ggplot(Y2008 %>% filter(Werksnummer==1111),aes(x=ID_Komponente,y=Defect)) + stat_pareto()+ labs(title="Y2008_1111")

Y2008_1121 <- ggplot(Y2008 %>% filter(Werksnummer==1121),aes(x=ID_Komponente,y=Defect)) + stat_pareto()+ labs(title="Y2008_1121")

Y2008_1122 <- ggplot(Y2008 %>% filter(Werksnummer==1122),aes(x=ID_Komponente,y=Defect)) + stat_pareto()+ labs(title="Y2008_1122")

Y2008_1132 <- ggplot(Y2008 %>% filter(Werksnummer==1132),aes(x=ID_Komponente,y=Defect)) + stat_pareto()+ labs(title="Y2008_1132")

Y2008_1142 <- ggplot(Y2008 %>% filter(Werksnummer==1142),aes(x=ID_Komponente,y=Defect)) + stat_pareto()+ labs(title="Y2008_1142")


```
``` {r Pareto Charts 2009, eval=FALSE, include=FALSE}
Y2009_1011 <- ggplot(Y2009 %>% filter(Werksnummer==1011),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2009_1011")

Y2009_1021 <- ggplot(Y2009 %>% filter(Werksnummer==1021),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2009_1021")

Y2009_1031 <- ggplot(Y2009 %>% filter(Werksnummer==1031),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2009_1031")

Y2009_1041 <- ggplot(Y2009 %>% filter(Werksnummer==1041),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2009_1041")

Y2009_1051 <- ggplot(Y2009 %>% filter(Werksnummer==1051),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2009_1051")

Y2009_1061 <- ggplot(Y2009 %>% filter(Werksnummer==1061),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2009_1061")

Y2009_1071 <- ggplot(Y2009 %>% filter(Werksnummer==1071),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2009_1071")

Y2009_1072 <- ggplot(Y2009 %>% filter(Werksnummer==1072),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2009_1072")

Y2009_1081 <- ggplot(Y2009 %>% filter(Werksnummer==1081),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2009_1081")

Y2009_1082 <- ggplot(Y2009 %>% filter(Werksnummer==1082),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2009_1082")

Y2009_1091 <- ggplot(Y2009 %>% filter(Werksnummer==1091),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2009_1091")

Y2009_1092 <- ggplot(Y2009 %>% filter(Werksnummer==1092),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2009_1092")

Y2009_1111 <- ggplot(Y2009 %>% filter(Werksnummer==1111),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2009_1111")

Y2009_1121 <- ggplot(Y2009 %>% filter(Werksnummer==1121),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2009_1121")

Y2009_1122 <- ggplot(Y2009 %>% filter(Werksnummer==1122),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2009_1122")

Y2009_1132 <- ggplot(Y2009 %>% filter(Werksnummer==1132),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2009_1132")

Y2009_1142 <- ggplot(Y2009 %>% filter(Werksnummer==1142),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2009_1142")


```
``` {r Pareto Charts 2010, eval=FALSE, include=FALSE}
Y2010_1011 <- ggplot(Y2010 %>% filter(Werksnummer==1011),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2010_1011")

Y2010_1021 <- ggplot(Y2010 %>% filter(Werksnummer==1021),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2010_1021")

Y2010_1031 <- ggplot(Y2010 %>% filter(Werksnummer==1031),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2010_1031")

Y2010_1041 <- ggplot(Y2010 %>% filter(Werksnummer==1041),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2010_1041")

Y2010_1051 <- ggplot(Y2010 %>% filter(Werksnummer==1051),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2010_1051")

Y2010_1061 <- ggplot(Y2010 %>% filter(Werksnummer==1061),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2010_1061")

Y2010_1071 <- ggplot(Y2010 %>% filter(Werksnummer==1071),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2010_1071")

Y2010_1072 <- ggplot(Y2010 %>% filter(Werksnummer==1072),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2010_1072")

Y2010_1081 <- ggplot(Y2010 %>% filter(Werksnummer==1081),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2010_1081")

Y2010_1082 <- ggplot(Y2010 %>% filter(Werksnummer==1082),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2010_1082")

Y2010_1091 <- ggplot(Y2010 %>% filter(Werksnummer==1091),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2010_1091")

Y2010_1092 <- ggplot(Y2010 %>% filter(Werksnummer==1092),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2010_1092")

Y2010_1111 <- ggplot(Y2010 %>% filter(Werksnummer==1111),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2010_1111")

Y2010_1121 <- ggplot(Y2010 %>% filter(Werksnummer==1121),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2010_1211")

Y2010_1122 <- ggplot(Y2010 %>% filter(Werksnummer==1122),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2010_1122")

Y2010_1132 <- ggplot(Y2010 %>% filter(Werksnummer==1132),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2010_1132")

Y2010_1142 <- ggplot(Y2010 %>% filter(Werksnummer==1142),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2010_1142")


```
``` {r Pareto Charts 2011, eval=FALSE, include=FALSE}
Y2011_1011 <- ggplot(Y2011 %>% filter(Werksnummer==1011),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2011_1011")

Y2011_1021 <- ggplot(Y2011 %>% filter(Werksnummer==1021),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2011_1021")

Y2011_1031 <- ggplot(Y2011 %>% filter(Werksnummer==1031),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2011_1031")

Y2011_1041 <- ggplot(Y2011 %>% filter(Werksnummer==1041),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2011_1041")

Y2011_1051 <- ggplot(Y2011 %>% filter(Werksnummer==1051),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2011_1051")

Y2011_1061 <- ggplot(Y2011 %>% filter(Werksnummer==1061),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2011_1061")

Y2011_1071 <- ggplot(Y2011 %>% filter(Werksnummer==1071),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2011_1071")

Y2011_1072 <- ggplot(Y2011 %>% filter(Werksnummer==1072),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2011_1072")

Y2011_1081 <- ggplot(Y2011 %>% filter(Werksnummer==1081),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2011_1081")

Y2011_1082 <- ggplot(Y2011 %>% filter(Werksnummer==1082),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2011_1082")

Y2011_1091 <- ggplot(Y2011 %>% filter(Werksnummer==1091),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2011_1091")

Y2011_1092 <- ggplot(Y2011 %>% filter(Werksnummer==1092),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2011_1092")

Y2011_1111 <- ggplot(Y2011 %>% filter(Werksnummer==1111),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2011_1111")

Y2011_1121 <- ggplot(Y2011 %>% filter(Werksnummer==1121),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2011_1121")

Y2011_1122 <- ggplot(Y2011 %>% filter(Werksnummer==1122),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2011_1122")

Y2011_1132 <- ggplot(Y2011 %>% filter(Werksnummer==1132),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2011_1132")

Y2011_1142 <- ggplot(Y2011 %>% filter(Werksnummer==1142),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2011_1142")


```
``` {r Pareto Charts 2012, eval=FALSE, include=FALSE}
Y2012_1011 <- ggplot(Y2012 %>% filter(Werksnummer==1011),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2012_1011")

Y2012_1021 <- ggplot(Y2012 %>% filter(Werksnummer==1021),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2012_1021")

Y2012_1031 <- ggplot(Y2012 %>% filter(Werksnummer==1031),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2012_1031")

Y2012_1041 <- ggplot(Y2012 %>% filter(Werksnummer==1041),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2012_1041")

Y2012_1051 <- ggplot(Y2012 %>% filter(Werksnummer==1051),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2012_1051")

Y2012_1061 <- ggplot(Y2012 %>% filter(Werksnummer==1061),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2012_1061")

Y2012_1071 <- ggplot(Y2012 %>% filter(Werksnummer==1071),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2012_1071")

Y2012_1072 <- ggplot(Y2012 %>% filter(Werksnummer==1072),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2012_1072")

Y2012_1081 <- ggplot(Y2012 %>% filter(Werksnummer==1081),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2012_1081")

Y2012_1082 <- ggplot(Y2012 %>% filter(Werksnummer==1082),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2012_1082")

Y2012_1091 <- ggplot(Y2012 %>% filter(Werksnummer==1091),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2012_1091")

Y2012_1092 <- ggplot(Y2012 %>% filter(Werksnummer==1092),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2012_1092")

Y2012_1111 <- ggplot(Y2012 %>% filter(Werksnummer==1111),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2012_1111")

Y2012_1121 <- ggplot(Y2012 %>% filter(Werksnummer==1121),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2012_1121")

Y2012_1122 <- ggplot(Y2012 %>% filter(Werksnummer==1122),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2012_1122")

Y2012_1132 <- ggplot(Y2012 %>% filter(Werksnummer==1132),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2012_1132")

Y2012_1141 <- ggplot(Y2012 %>% filter(Werksnummer==1141),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2012_1141")

Y2012_1142 <- ggplot(Y2012 %>% filter(Werksnummer==1142),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2012_1142")


```
``` {r Pareto Charts 2013, eval=FALSE, include=FALSE}
Y2013_1011 <- ggplot(Y2013 %>% filter(Werksnummer==1011),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2013_1011")

Y2013_1021 <- ggplot(Y2013 %>% filter(Werksnummer==1021),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2013_1021")

Y2013_1031 <- ggplot(Y2013 %>% filter(Werksnummer==1031),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2013_1031")

Y2013_1041 <- ggplot(Y2013 %>% filter(Werksnummer==1041),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2013_1041")

Y2013_1051 <- ggplot(Y2013 %>% filter(Werksnummer==1051),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2013_1051")

Y2013_1061 <- ggplot(Y2013 %>% filter(Werksnummer==1061),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2013_1061")

Y2013_1071 <- ggplot(Y2013 %>% filter(Werksnummer==1071),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2013_1071")

Y2013_1072 <- ggplot(Y2013 %>% filter(Werksnummer==1072),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2013_1072")

Y2013_1081 <- ggplot(Y2013 %>% filter(Werksnummer==1081),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2013_1081")

Y2013_1082 <- ggplot(Y2013 %>% filter(Werksnummer==1082),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2013_1081")

Y2013_1091 <- ggplot(Y2013 %>% filter(Werksnummer==1091),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2013_1091")

Y2013_1092 <- ggplot(Y2013 %>% filter(Werksnummer==1092),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2013_1092")

Y2013_1101 <- ggplot(Y2013 %>% filter(Werksnummer==1101),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2013_1102")

Y2013_1111 <- ggplot(Y2013 %>% filter(Werksnummer==1111),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2013_1111")

Y2013_1122 <- ggplot(Y2013 %>% filter(Werksnummer==1122),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2013_1122")

Y2013_1131 <- ggplot(Y2013 %>% filter(Werksnummer==1131),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2013_131")

Y2013_1132 <- ggplot(Y2013 %>% filter(Werksnummer==1132),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2013_1132")

Y2013_1141 <- ggplot(Y2013 %>% filter(Werksnummer==1141),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2013_1141")


```
``` {r Pareto Charts 2014, eval=FALSE, include=FALSE}
Y2014_1011 <- ggplot(Y2014 %>% filter(Werksnummer==1011),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2014_1011")

Y2014_1021 <- ggplot(Y2014 %>% filter(Werksnummer==1021),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2014_1021")

Y2014_1031 <- ggplot(Y2014 %>% filter(Werksnummer==1031),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2014_1031")

Y2014_1041 <- ggplot(Y2014 %>% filter(Werksnummer==1041),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2014_1041")

Y2014_1051 <- ggplot(Y2014 %>% filter(Werksnummer==1051),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2014_1051")

Y2014_1061 <- ggplot(Y2014 %>% filter(Werksnummer==1061),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2014_1061")

Y2014_1071 <- ggplot(Y2014 %>% filter(Werksnummer==1071),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2014_1071")

Y2014_1072 <- ggplot(Y2014 %>% filter(Werksnummer==1072),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2014_1072")

Y2014_1081 <- ggplot(Y2014 %>% filter(Werksnummer==1081),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2014_1081")

Y2014_1082 <- ggplot(Y2014 %>% filter(Werksnummer==1082),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2014_1082")

Y2014_1091 <- ggplot(Y2014 %>% filter(Werksnummer==1091),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2014_1091")

Y2014_1092 <- ggplot(Y2014 %>% filter(Werksnummer==1092),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2014_1092")

Y2014_1111 <- ggplot(Y2014 %>% filter(Werksnummer==1111),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2014_1111")

Y2014_1101 <- ggplot(Y2014 %>% filter(Werksnummer==1101),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2014_1101")

Y2014_1131 <- ggplot(Y2014 %>% filter(Werksnummer==1131),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2014_1131")

Y2014_1132 <- ggplot(Y2014 %>% filter(Werksnummer==1132),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2014_1132")

Y2014_1141 <- ggplot(Y2014 %>% filter(Werksnummer==1141),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2014_1141")


```
``` {r Pareto Charts 2015, eval=FALSE, include=FALSE}
Y2015_1011 <- ggplot(Y2015 %>% filter(Werksnummer==1011),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2015_1011")

Y2015_1021 <- ggplot(Y2015 %>% filter(Werksnummer==1021),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2015_1021")

Y2015_1031 <- ggplot(Y2015 %>% filter(Werksnummer==1031),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2015_1031")

Y2015_1041 <- ggplot(Y2015 %>% filter(Werksnummer==1041),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2015_1041")

Y2015_1051 <- ggplot(Y2015 %>% filter(Werksnummer==1051),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2015_1051")

Y2015_1061 <- ggplot(Y2015 %>% filter(Werksnummer==1061),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2015_1061")

Y2015_1071 <- ggplot(Y2015 %>% filter(Werksnummer==1071),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2015_1071")

Y2015_1072 <- ggplot(Y2015 %>% filter(Werksnummer==1072),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2015_1072")

Y2015_1081 <- ggplot(Y2015 %>% filter(Werksnummer==1081),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2015_1081")

Y2015_1082 <- ggplot(Y2015 %>% filter(Werksnummer==1082),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2015_1082")

Y2015_1091 <- ggplot(Y2015 %>% filter(Werksnummer==1091),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2015_1091")

Y2015_1092 <- ggplot(Y2015 %>% filter(Werksnummer==1092),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2015_1092")

Y2015_1111 <- ggplot(Y2015 %>% filter(Werksnummer==1111),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2015_1111")

Y2015_1101 <- ggplot(Y2015 %>% filter(Werksnummer==1101),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2015_1101")

Y2015_1131 <- ggplot(Y2015 %>% filter(Werksnummer==1131),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2015_1131")

Y2015_1132 <- ggplot(Y2015 %>% filter(Werksnummer==1132),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2015_1132")

Y2015_1141 <- ggplot(Y2015 %>% filter(Werksnummer==1141),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2015_1141")


```
``` {r Pareto Charts 2016, eval=FALSE, include=FALSE}
Y2016_1011 <- ggplot(Y2016 %>% filter(Werksnummer==1011),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2016_1011")

Y2016_1021 <- ggplot(Y2016 %>% filter(Werksnummer==1021),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2016_1021")

Y2016_1031 <- ggplot(Y2016 %>% filter(Werksnummer==1031),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2016_1031")

Y2016_1041 <- ggplot(Y2016 %>% filter(Werksnummer==1041),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2016_1041")

Y2016_1051 <- ggplot(Y2016 %>% filter(Werksnummer==1051),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2016_1051")

Y2016_1061 <- ggplot(Y2016 %>% filter(Werksnummer==1061),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2016_1061")

Y2016_1071 <- ggplot(Y2016 %>% filter(Werksnummer==1071),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2016_1071")

Y2016_1072 <- ggplot(Y2016 %>% filter(Werksnummer==1072),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2016_1072")

Y2016_1081 <- ggplot(Y2016 %>% filter(Werksnummer==1081),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2016_1081")

Y2016_1082 <- ggplot(Y2016 %>% filter(Werksnummer==1082),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2016_1082")

Y2016_1091 <- ggplot(Y2016 %>% filter(Werksnummer==1091),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2016_1091")

Y2016_1092 <- ggplot(Y2016 %>% filter(Werksnummer==1092),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2016_1092")

Y2016_1111 <- ggplot(Y2016 %>% filter(Werksnummer==1111),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2016_1111")

Y2016_1101 <- ggplot(Y2016 %>% filter(Werksnummer==1101),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2016_1101")

Y2016_1132 <- ggplot(Y2016 %>% filter(Werksnummer==1132),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2016_1132")

Y2016_1141 <- ggplot(Y2016 %>% filter(Werksnummer==1141),aes(x=ID_Komponente,y=Defect)) + stat_pareto() + labs(title="Y2016_1141")


```
```{r 2008-Monthly Plots, eval=FALSE, include=FALSE}
Y2008_K7_ <- ggplot(Y2008_K7) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2008_K7")

Y2008_K6_ <- ggplot(Y2008_K6) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2008_K6")

Y2008_K5_ <- ggplot(Y2008_K5) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2008_K5")

Y2008_K4_ <- ggplot(Y2008_K4) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2008_K4")

Y2008_K3SG2_ <- ggplot(Y2008_K3SG2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2008_K3SG2")

Y2008_K3SG1_ <- ggplot(Y2008_K3SG1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2008_K3SG1")

Y2008_K3AG2_ <- ggplot(Y2008_K3AG2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2008_K3AG2")

Y2008_K3AG1_ <- ggplot(Y2008_K3AG1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2008_K3AG1")

Y2008_K2ST2_ <- ggplot(Y2008_K2ST2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2008_K2ST2")

Y2008_K2ST1_ <- ggplot(Y2008_K2ST1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2008_K2ST1")

Y2008_K2LE2_ <- ggplot(Y2008_K2LE2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2008_K2LE2")

Y2008_K2LE1_ <- ggplot(Y2008_K2LE1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2008_K2LE1")

Y2008_K1DI2_ <- ggplot(Y2008_K1DI2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2008_K1DI2")

Y2008_K1DI1_ <- ggplot(Y2008_K1DI1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2008_K1DI1")

Y2008_K1BE2_ <- ggplot(Y2008_K1BE2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2008_K1BE2")

Y2008_K1BE1_ <- ggplot(Y2008_K1BE1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2008_K1BE1")
```
```{r 2009-Monthly Plots, eval=FALSE, include=FALSE}
Y2009_K7_ <- ggplot(Y2009_K7) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2009_K7")

Y2009_K6_ <- ggplot(Y2009_K6) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2009_K6")

Y2009_K5_ <- ggplot(Y2009_K5) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2009_K5")

Y2009_K4_ <- ggplot(Y2009_K4) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2009_K4")

Y2009_K3SG2_ <- ggplot(Y2009_K3SG2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2009_K3SG2")

Y2009_K3SG1_ <- ggplot(Y2009_K3SG1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2009_K3SG1")

Y2009_K3AG2_ <- ggplot(Y2009_K3AG2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2009_K3AG2")

Y2009_K3AG1_ <- ggplot(Y2009_K3AG1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2009_K3AG1")

Y2009_K2ST2_ <- ggplot(Y2009_K2ST2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2009_K2ST2")

Y2009_K2ST1_ <- ggplot(Y2009_K2ST1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2009_K2ST1")

Y2009_K2LE2_ <- ggplot(Y2009_K2LE2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2009_K2LE2")

Y2009_K2LE1_ <- ggplot(Y2009_K2LE1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2009_K2LE1")

Y2009_K1DI2_ <- ggplot(Y2009_K1DI2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2009_K1DI2")

Y2009_K1DI1_ <- ggplot(Y2009_K1DI1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2009_K1DI1")

Y2009_K1BE2_ <- ggplot(Y2009_K1BE2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2009_K1BE2")

Y2009_K1BE1_ <- ggplot(Y2009_K1BE1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2009_K1BE1")
```
```{r 2010-Monthly Plots, eval=FALSE, include=FALSE}
Y2010_K7_ <- ggplot(Y2010_K7) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2010_K7")

Y2010_K6_ <- ggplot(Y2010_K6) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2010_K6")

Y2010_K5_ <- ggplot(Y2010_K5) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2010_K5")

Y2010_K4_ <- ggplot(Y2010_K4) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2010_K4")

Y2010_K3SG2_ <- ggplot(Y2010_K3SG2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2010_K3SG2")

Y2010_K3SG1_ <- ggplot(Y2010_K3SG1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2010_K3SG1")

Y2010_K3AG2_ <- ggplot(Y2010_K3AG2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2010_K3AG2")

Y2010_K3AG1_ <- ggplot(Y2010_K3AG1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2010_K3AG1")

Y2010_K2ST2_ <- ggplot(Y2010_K2ST2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2010_K2ST2")

Y2010_K2ST1_ <- ggplot(Y2010_K2ST1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2010_K2ST1")

Y2010_K2LE2_ <- ggplot(Y2010_K2LE2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2010_K2LE2")

Y2010_K2LE1_ <- ggplot(Y2010_K2LE1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2010_K2LE1")

Y2010_K1DI2_ <- ggplot(Y2010_K1DI2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2010_K1DI2")

Y2010_K1DI1_ <- ggplot(Y2010_K1DI1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2010_K1DI1")

Y2010_K1BE2_ <- ggplot(Y2010_K1BE2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2010_K1BE2")

Y2010_K1BE1_ <- ggplot(Y2010_K1BE1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2010_K1BE1")
```
```{r 2011-Monthly Plots, eval=FALSE, include=FALSE}
Y2011_K7_ <- ggplot(Y2011_K7) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2011_K7")

Y2011_K6_ <- ggplot(Y2011_K6) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2011_K6")

Y2011_K5_ <- ggplot(Y2011_K5) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2011_K5")

Y2011_K4_ <- ggplot(Y2011_K4) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2011_K4")

Y2011_K3SG2_ <- ggplot(Y2011_K3SG2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2011_K3SG2")

Y2011_K3SG1_ <- ggplot(Y2011_K3SG1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2011_K3SG1")

Y2011_K3AG2_ <- ggplot(Y2011_K3AG2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2011_K3AG2")

Y2011_K3AG1_ <- ggplot(Y2011_K3AG1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2011_K3AG1")

Y2011_K2ST2_ <- ggplot(Y2011_K2ST2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2011_K2ST2")

Y2011_K2ST1_ <- ggplot(Y2011_K2ST1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2011_K2ST1")

Y2011_K2LE2_ <- ggplot(Y2011_K2LE2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2011_K2LE2")

Y2011_K2LE1_ <- ggplot(Y2011_K2LE1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2011_K2LE1")

Y2011_K1DI2_ <- ggplot(Y2011_K1DI2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2011_K1DI2")

Y2011_K1DI1_ <- ggplot(Y2011_K1DI1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2011_K1DI1")

Y2011_K1BE2_ <- ggplot(Y2011_K1BE2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2011_K1BE2")

Y2011_K1BE1_ <- ggplot(Y2011_K1BE1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2011_K1BE1")
```
```{r 2012-Monthly Plots, eval=FALSE, include=FALSE}
Y2012_K7_ <- ggplot(Y2012_K7) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2012_K7")

Y2012_K6_ <- ggplot(Y2012_K6) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2012_K6")

Y2012_K5_ <- ggplot(Y2012_K5) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2012_K5")

Y2012_K4_ <- ggplot(Y2012_K4) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2012_K4")

Y2012_K3SG2_ <- ggplot(Y2012_K3SG2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2012_K3SG2")

Y2012_K3SG1_ <- ggplot(Y2012_K3SG1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2012_K3SG1")

Y2012_K3AG2_ <- ggplot(Y2012_K3AG2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2012_K3AG2")

Y2012_K3AG1_ <- ggplot(Y2012_K3AG1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2012_K3AG1")

Y2012_K2ST2_ <- ggplot(Y2012_K2ST2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2012_K2ST2")

Y2012_K2ST1_ <- ggplot(Y2012_K2ST1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2012_K2ST1")

Y2012_K2LE2_ <- ggplot(Y2012_K2LE2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2012_K2LE2")

Y2012_K2LE1_ <- ggplot(Y2012_K2LE1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2012_K2LE1")

Y2012_K1DI2_ <- ggplot(Y2012_K1DI2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2012_K1DI2")

Y2012_K1DI1_ <- ggplot(Y2012_K1DI1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2012_K1DI1")

Y2012_K1BE2_ <- ggplot(Y2012_K1BE2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2012_K1BE2")

Y2012_K1BE1_ <- ggplot(Y2012_K1BE1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2012_K1BE1")
```
```{r 2013-Monthly Plots, eval=FALSE, include=FALSE}
Y2013_K7_ <- ggplot(Y2013_K7) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2013_K7")

Y2013_K6_ <- ggplot(Y2013_K6) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2013_K6")

Y2013_K5_ <- ggplot(Y2013_K5) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2013_K5")

Y2013_K4_ <- ggplot(Y2013_K4) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2013_K4")

Y2013_K3SG2_ <- ggplot(Y2013_K3SG2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2013_K3SG2")

Y2013_K3SG1_ <- ggplot(Y2013_K3SG1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2013_K3SG1")

Y2013_K3AG2_ <- ggplot(Y2013_K3AG2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2013_K3AG2")

Y2013_K3AG1_ <- ggplot(Y2013_K3AG1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2013_K3AG1")

Y2013_K2ST2_ <- ggplot(Y2013_K2ST2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2013_K2ST2")

Y2013_K2ST1_ <- ggplot(Y2013_K2ST1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2013_K2ST1")

Y2013_K2LE2_ <- ggplot(Y2013_K2LE2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2013_K2LE2")

Y2013_K2LE1_ <- ggplot(Y2013_K2LE1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2013_K2LE1")

Y2013_K1DI2_ <- ggplot(Y2013_K1DI2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2013_K1DI2")

Y2013_K1DI1_ <- ggplot(Y2013_K1DI1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2013_K1DI1")

Y2013_K1BE2_ <- ggplot(Y2013_K1BE2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2013_K1BE2")

Y2013_K1BE1_ <- ggplot(Y2013_K1BE1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2013_K1BE1")
```
```{r 2014-Monthly Plot, eval=FALSE, include=FALSE}
Y2014_K7_ <- ggplot(Y2014_K7) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2014_K7")

Y2014_K6_ <- ggplot(Y2014_K6) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2014_K6")

Y2014_K5_ <- ggplot(Y2014_K5) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2014_K5")

Y2014_K4_ <- ggplot(Y2014_K4) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2014_K4")

Y2014_K3SG2_ <- ggplot(Y2014_K3SG2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2014_K3SG2")

Y2014_K3SG1_ <- ggplot(Y2014_K3SG1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2014_K3SG1")

Y2014_K3AG2_ <- ggplot(Y2014_K3AG2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2014_K3AG2")

Y2014_K3AG1_ <- ggplot(Y2014_K3AG1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2014_K3AG1")

Y2014_K2ST2_ <- ggplot(Y2014_K2ST2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2014_K2ST2")

Y2014_K2ST1_ <- ggplot(Y2014_K2ST1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2014_K2ST1")

Y2014_K2LE2_ <- ggplot(Y2014_K2LE2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2014_K2LE2")

Y2014_K2LE1_ <- ggplot(Y2014_K2LE1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2014_K2LE1")

Y2014_K1DI2_ <- ggplot(Y2014_K1DI2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2014_K1DI2")

Y2014_K1DI1_ <- ggplot(Y2014_K1DI1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2014_K1DI1")

Y2014_K1BE2_ <- ggplot(Y2014_K1BE2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2014_K1BE2")

Y2014_K1BE1_ <- ggplot(Y2014_K1BE1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2014_K1BE1")
```
```{r 2015-Monthly Plot, eval=FALSE, include=FALSE}
Y2015_K7_ <- ggplot(Y2015_K7) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2015_K7")

Y2015_K6_ <- ggplot(Y2015_K6) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2015_K6")

Y2015_K5_ <- ggplot(Y2015_K5) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2015_K5")

Y2015_K4_ <- ggplot(Y2015_K4) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2015_K4")

Y2015_K3SG2_ <- ggplot(Y2015_K3SG2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2015_K3SG2")

Y2015_K3SG1_ <- ggplot(Y2015_K3SG1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2015_K3SG1")

Y2015_K3AG2_ <- ggplot(Y2015_K3AG2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2015_K3AG2")

Y2015_K3AG1_ <- ggplot(Y2015_K3AG1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2015_K3AG1")

Y2015_K2ST2_ <- ggplot(Y2015_K2ST2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2015_K2ST2")

Y2015_K2ST1_ <- ggplot(Y2015_K2ST1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2015_K2ST1")

Y2015_K2LE2_ <- ggplot(Y2015_K2LE2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2015_K2LE2")

Y2015_K2LE1_ <- ggplot(Y2015_K2LE1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2015_K2LE1")

Y2015_K1DI2_ <- ggplot(Y2015_K1DI2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2015_K1DI2")

Y2015_K1DI1_ <- ggplot(Y2015_K1DI1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2015_K1DI1")

Y2015_K1BE2_ <- ggplot(Y2015_K1BE2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2015_K1BE2")

Y2015_K1BE1_ <- ggplot(Y2015_K1BE1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2015_K1BE1")
```
```{r 2016-Monthly Plot, eval=FALSE, include=FALSE}
Y2016_K7_ <- ggplot(Y2016_K7) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2016_K7")

Y2016_K6_ <- ggplot(Y2016_K6) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2016_K6")

Y2016_K5_ <- ggplot(Y2016_K5) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2016_K5")

Y2016_K4_ <- ggplot(Y2016_K4) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2016_K4")

Y2016_K3SG2_ <- ggplot(Y2016_K3SG2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2016_K3SG2")

Y2016_K3SG1_ <- ggplot(Y2016_K3SG1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2016_K3SG1")

Y2016_K3AG2_ <- ggplot(Y2016_K3AG2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2016_K3AG2")

Y2016_K3AG1_ <- ggplot(Y2016_K3AG1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2016_K3AG1")

Y2016_K2ST2_ <- ggplot(Y2016_K2ST2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2016_K2ST2")

Y2016_K2ST1_ <- ggplot(Y2016_K2ST1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2016_K2ST1")

Y2016_K2LE2_ <- ggplot(Y2016_K2LE2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2016_K2LE2")

Y2016_K2LE1_ <- ggplot(Y2016_K2LE1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2016_K2LE1")

Y2016_K1DI2_ <- ggplot(Y2016_K1DI2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2016_K1DI2")

Y2016_K1DI1_ <- ggplot(Y2016_K1DI1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2016_K1DI1")

Y2016_K1BE2_ <- ggplot(Y2016_K1BE2) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2016_K1BE2")

Y2016_K1BE1_ <- ggplot(Y2016_K1BE1) + geom_point(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_line(aes(x=Produktionsdatum,y=Defect,color=Werksnummer,group=Werksnummer)) + geom_point(aes(x=Produktionsdatum,y=cumulative,colour="Cumulative Defects")) + labs(title="Y2016_K1BE1")
```

#                                         <b> SHINY APPLICATION </b>


<b> User Manual: </b>

Kindly Select the Year Using the slider and select a  Werksnummer to display the <b> Pareto Chart </b> which would display the Error freqeuncies of Components produced in the selected Factory and the Selected Year.

Kindly Select the Year Using the slider and select a Komponents ID to display the <b> INTERACTIVE - Line Diagram </b> indicating the Defects of the selected component over the year, the line diagram will indicate each of the component producing factories with a seperate line and it will aslo display the cumulative defects for the year split into months. <b> Kindly hover over the data points to get an interavtive view of the data values </b> 

<b> Note: </b>

Werksnummer is indicated by 1011,1021,1092,.. etc.,

Component ID's are indicated by K4,K5, K4,K3SG2,.. etc.,

<b> Additioanl Note :</b>

If a Chart is not displayed for a selected option, it would mean that the Selected Factory Did not produce components in that particular selected year.
```{r Shiny App, echo=FALSE, message=FALSE, warning=FALSE}


ui <- fluidPage(
  titlePanel("Input Menu:"),
  sidebarLayout(
    sidebarPanel(
      selectInput(inputId = "Werksnummer", "Select a Werksnummer for the Pareto Chart: ", choices = list("1011" ,"1021", "1031", "1041", "1051", "1061", "1071", "1072", "1081", "1082", "1091", "1092", "1111","1011", "1101", "1121", "1122", "1132", "1141", "1142")), 
      
      selectInput(inputId = "Komponente", "Select a Component for the Interactive Line Diagram: ", choices = list("K4" ,"K5", "K6", "K7","K3SG2", "K3SG1", "K3AG2", "K3AG1","K2ST2", "K2ST1", "K2LE2", "K2LE1", "K1DI2", "K1DI1", "K1BE2", "K1BE1")),
      
      sliderInput("slider1", h3("Select Year"),
                       min = 2008, max = 2016, value = 2016,step=1),width=6),
  
    
    
    
  mainPanel("PARETO CHARTS FOR INDIVIDUAL FACTORIES   ..................................................................................................................................  INTERACTIVE - LINE DIAGRAMS FOR INDIVIDUAL COMPONENTS",
                          fluidRow(
                            splitLayout(cellWidths = c("80%", "80%"), plotOutput("plot1",width="100%",height= "600px"), plotlyOutput("plot2",,width="100%",height= "600px"))
                          )
                )
  ))



server <- function(input, output) {
  output$plot1 <- renderPlot({
    
    if(input$slider1 == 2008 & input$Werksnummer == "1011"){
      Y2008_1011
    }
    else if(input$slider1 == 2008 & input$Werksnummer == "1021"){
      Y2008_1021
    }
    else if(input$slider1 == 2008 & input$Werksnummer == "1031"){
      Y2008_1031
    }
    else if(input$slider1 == 2008 & input$Werksnummer == "1041"){
      Y2008_1041
    }
    else if(input$slider1 == 2008 & input$Werksnummer == "1041"){
      Y2008_1041
    }
    else if(input$slider1 == 2008 & input$Werksnummer == "1051"){
      Y2008_1051
    }
    else if(input$slider1 == 2008 & input$Werksnummer == "1061"){
      Y2008_1061
    }
    else if(input$slider1 == 2008 & input$Werksnummer == "1071"){
      Y2008_1071
    }
    else if(input$slider1 == 2008 & input$Werksnummer == "1072"){
      Y2008_1072
    }
    else if(input$slider1 == 2008 & input$Werksnummer == "1081"){
      Y2008_1081
    }
    else if(input$slider1 == 2008 & input$Werksnummer == "1082"){
      Y2008_1082
    }
    else if(input$slider1 == 2008 & input$Werksnummer == "1091"){
      Y2008_1091
    }
    else if(input$slider1 == 2008 & input$Werksnummer == "1092"){
      Y2008_1092
    }
    else if(input$slider1 == 2008 & input$Werksnummer == "1111"){
      Y2008_1111
    }
   else if(input$slider1 == 2008 & input$Werksnummer == "1121"){
      Y2008_1121
   }
    else if(input$slider1 == 2008 & input$Werksnummer == "1122"){
      Y2008_1122
    }
    else if(input$slider1 == 2008 & input$Werksnummer == "1132"){
      Y2008_1132
    }
    else if(input$slider1 == 2008 & input$Werksnummer == "1142"){
      Y2008_1142
    }
    
    else if(input$slider1 == 2009 & input$Werksnummer == "1011"){
      Y2009_1011
    }
    else if(input$slider1 == 2009 & input$Werksnummer == "1021"){
      Y2009_1021
    }
    else if(input$slider1 == 2009 & input$Werksnummer == "1031"){
      Y2009_1031
    }
    else if(input$slider1 == 2009 & input$Werksnummer == "1041"){
      Y2009_1041
    }
    else if(input$slider1 == 2009 & input$Werksnummer == "1041"){
      Y2009_1041
    }
    else if(input$slider1 == 2009 & input$Werksnummer == "1051"){
      Y2009_1051
    }
    else if(input$slider1 == 2009 & input$Werksnummer == "1061"){
      Y2009_1061
    }
    else if(input$slider1 == 2009 & input$Werksnummer == "1071"){
      Y2009_1071
    }
    else if(input$slider1 == 2009 & input$Werksnummer == "1072"){
      Y2009_1072
    }
    else if(input$slider1 == 2009 & input$Werksnummer == "1081"){
      Y2009_1081
    }
    else if(input$slider1 == 2009 & input$Werksnummer == "1082"){
      Y2009_1082
    }
    else if(input$slider1 == 2009 & input$Werksnummer == "1091"){
      Y2009_1091
    }
    else if(input$slider1 == 2009 & input$Werksnummer == "1092"){
      Y2009_1092
    }
    else if(input$slider1 == 2009 & input$Werksnummer == "1111"){
      Y2009_1111
    }
   else if(input$slider1 == 2009 & input$Werksnummer == "1121"){
      Y2009_1121
   }
    else if(input$slider1 == 2009 & input$Werksnummer == "1122"){
      Y2009_1122
    }
    else if(input$slider1 == 2009 & input$Werksnummer == "1132"){
      Y2009_1132
    }
    else if(input$slider1 == 2009 & input$Werksnummer == "1142"){
      Y2009_1142
    }
    
    else if(input$slider1 == 2010 & input$Werksnummer == "1011"){
      Y2010_1011
    }
    else if(input$slider1 == 2010 & input$Werksnummer == "1021"){
      Y2010_1021
    }
    else if(input$slider1 == 2010 & input$Werksnummer == "1031"){
      Y2010_1031
    }
    else if(input$slider1 == 2010 & input$Werksnummer == "1041"){
      Y2010_1041
    }
    else if(input$slider1 == 2010 & input$Werksnummer == "1041"){
      Y2010_1041
    }
    else if(input$slider1 == 2010 & input$Werksnummer == "1051"){
      Y2010_1051
    }
    else if(input$slider1 == 2010 & input$Werksnummer == "1061"){
      Y2010_1061
    }
    else if(input$slider1 == 2010 & input$Werksnummer == "1071"){
      Y2010_1071
    }
    else if(input$slider1 == 2010 & input$Werksnummer == "1072"){
      Y2010_1072
    }
    else if(input$slider1 == 2010 & input$Werksnummer == "1081"){
      Y2010_1081
    }
    else if(input$slider1 == 2010 & input$Werksnummer == "1082"){
      Y2010_1082
    }
    else if(input$slider1 == 2010 & input$Werksnummer == "1091"){
      Y2010_1091
    }
    else if(input$slider1 == 2010 & input$Werksnummer == "1092"){
      Y2010_1092
    }
    else if(input$slider1 == 2010 & input$Werksnummer == "1111"){
      Y2010_1111
    }
   else if(input$slider1 == 2010 & input$Werksnummer == "1121"){
      Y2010_1121
   }
    else if(input$slider1 == 2010 & input$Werksnummer == "1122"){
      Y2010_1122
    }
    else if(input$slider1 == 2010 & input$Werksnummer == "1132"){
      Y2010_1132
    }
    else if(input$slider1 == 2010 & input$Werksnummer == "1142"){
      Y2010_1142
    }
    
    else if(input$slider1 == 2011 & input$Werksnummer == "1011"){
      Y2011_1011
    }
    else if(input$slider1 == 2011 & input$Werksnummer == "1021"){
      Y2011_1021
    }
    else if(input$slider1 == 2011 & input$Werksnummer == "1031"){
      Y2011_1031
    }
    else if(input$slider1 == 2011 & input$Werksnummer == "1041"){
      Y2011_1041
    }
    else if(input$slider1 == 2011 & input$Werksnummer == "1041"){
      Y2011_1041
    }
    else if(input$slider1 == 2011 & input$Werksnummer == "1051"){
      Y2011_1051
    }
    else if(input$slider1 == 2011 & input$Werksnummer == "1061"){
      Y2011_1061
    }
    else if(input$slider1 == 2011 & input$Werksnummer == "1071"){
      Y2011_1071
    }
    else if(input$slider1 == 2011 & input$Werksnummer == "1072"){
      Y2011_1072
    }
    else if(input$slider1 == 2011 & input$Werksnummer == "1081"){
      Y2011_1081
    }
    else if(input$slider1 == 2011 & input$Werksnummer == "1082"){
      Y2011_1082
    }
    else if(input$slider1 == 2011 & input$Werksnummer == "1091"){
      Y2011_1091
    }
    else if(input$slider1 == 2011 & input$Werksnummer == "1092"){
      Y2011_1092
    }
    else if(input$slider1 == 2011 & input$Werksnummer == "1111"){
      Y2011_1111
    }
   else if(input$slider1 == 2011 & input$Werksnummer == "1121"){
      Y2011_1121
   }
    else if(input$slider1 == 2011 & input$Werksnummer == "1122"){
      Y2011_1122
    }
    else if(input$slider1 == 2011 & input$Werksnummer == "1132"){
      Y2011_1132
    }
    else if(input$slider1 == 2011 & input$Werksnummer == "1142"){
      Y2011_1142
    }
    
    else if(input$slider1 == 2012 & input$Werksnummer == "1011"){
      Y2012_1011
    }
    else if(input$slider1 == 2012 & input$Werksnummer == "1021"){
      Y2012_1021
    }
    else if(input$slider1 == 2012 & input$Werksnummer == "1031"){
      Y2012_1031
    }
    else if(input$slider1 == 2012 & input$Werksnummer == "1041"){
      Y2012_1041
    }
    else if(input$slider1 == 2012 & input$Werksnummer == "1041"){
      Y2012_1041
    }
    else if(input$slider1 == 2012 & input$Werksnummer == "1051"){
      Y2012_1051
    }
    else if(input$slider1 == 2012 & input$Werksnummer == "1061"){
      Y2012_1061
    }
    else if(input$slider1 == 2012 & input$Werksnummer == "1071"){
      Y2012_1071
    }
    else if(input$slider1 == 2012 & input$Werksnummer == "1072"){
      Y2012_1072
    }
    else if(input$slider1 == 2012 & input$Werksnummer == "1081"){
      Y2012_1081
    }
    else if(input$slider1 == 2012 & input$Werksnummer == "1082"){
      Y2012_1082
    }
    else if(input$slider1 == 2012 & input$Werksnummer == "1091"){
      Y2012_1091
    }
    else if(input$slider1 == 2012 & input$Werksnummer == "1092"){
      Y2012_1092
    }
    else if(input$slider1 == 2012 & input$Werksnummer == "1111"){
      Y2012_1111
    }
   else if(input$slider1 == 2012 & input$Werksnummer == "1121"){
      Y2012_1121
   }
    else if(input$slider1 == 2012 & input$Werksnummer == "1122"){
      Y2012_1122
    }
    else if(input$slider1 == 2012 & input$Werksnummer == "1132"){
      Y2012_1132
    }
    else if(input$slider1 == 2012 & input$Werksnummer == "1041"){
      Y2012_1041
    }
    else if(input$slider1 == 2012 & input$Werksnummer == "1142"){
      Y2012_1142
    }
    else if(input$slider1 == 2013 & input$Werksnummer == "1011"){
      Y2013_1011
    }
    else if(input$slider1 == 2013 & input$Werksnummer == "1021"){
      Y2013_1021
    }
    else if(input$slider1 == 2013 & input$Werksnummer == "1031"){
      Y2013_1031
    }
    else if(input$slider1 == 2013 & input$Werksnummer == "1041"){
      Y2013_1041
    }
    else if(input$slider1 == 2013 & input$Werksnummer == "1041"){
      Y2013_1041
    }
    else if(input$slider1 == 2013 & input$Werksnummer == "1051"){
      Y2013_1051
    }
    else if(input$slider1 == 2013 & input$Werksnummer == "1061"){
      Y2013_1061
    }
    else if(input$slider1 == 2013 & input$Werksnummer == "1071"){
      Y2013_1071
    }
    else if(input$slider1 == 2013 & input$Werksnummer == "1072"){
      Y2013_1072
    }
    else if(input$slider1 == 2013 & input$Werksnummer == "1081"){
      Y2013_1081
    }
    else if(input$slider1 == 2013 & input$Werksnummer == "1082"){
      Y2013_1082
    }
    else if(input$slider1 == 2013 & input$Werksnummer == "1091"){
      Y2013_1091
    }
    else if(input$slider1 == 2013 & input$Werksnummer == "1092"){
      Y2013_1092
    }
    else if(input$slider1 == 2013 & input$Werksnummer == "1111"){
      Y2013_1111
    }
   else if(input$slider1 == 2013 & input$Werksnummer == "1101"){
      Y2013_1101
   }
    else if(input$slider1 == 2013 & input$Werksnummer == "1122"){
      Y2013_1122
    }
    else if(input$slider1 == 2013 & input$Werksnummer == "1131"){
      Y2013_1131
    }
    else if(input$slider1 == 2013 & input$Werksnummer == "1132"){
      Y2013_1132
    }
    else if(input$slider1 == 2013 & input$Werksnummer == "1141"){
      Y2013_1141
    }
    else if(input$slider1 == 2014 & input$Werksnummer == "1011"){
      Y2014_1011
    }
    else if(input$slider1 == 2014 & input$Werksnummer == "1021"){
      Y2014_1021
    }
    else if(input$slider1 == 2014 & input$Werksnummer == "1031"){
      Y2014_1031
    }
    else if(input$slider1 == 2014 & input$Werksnummer == "1041"){
      Y2014_1041
    }
    else if(input$slider1 == 2014 & input$Werksnummer == "1041"){
      Y2014_1041
    }
    else if(input$slider1 == 2014 & input$Werksnummer == "1051"){
      Y2014_1051
    }
    else if(input$slider1 == 2014 & input$Werksnummer == "1061"){
      Y2014_1061
    }
    else if(input$slider1 == 2014 & input$Werksnummer == "1071"){
      Y2014_1071
    }
    else if(input$slider1 == 2014 & input$Werksnummer == "1072"){
      Y2014_1072
    }
    else if(input$slider1 == 2014 & input$Werksnummer == "1081"){
      Y2014_1081
    }
    else if(input$slider1 == 2014 & input$Werksnummer == "1082"){
      Y2014_1082
    }
    else if(input$slider1 == 2014 & input$Werksnummer == "1091"){
      Y2014_1091
    }
    else if(input$slider1 == 2014 & input$Werksnummer == "1092"){
      Y2014_1092
    }
    else if(input$slider1 == 2014 & input$Werksnummer == "1111"){
      Y2014_1111
    }
   else if(input$slider1 == 2014 & input$Werksnummer == "1101"){
      Y2014_1101
   }
    else if(input$slider1 == 2014 & input$Werksnummer == "1131"){
      Y2014_1131
    }
    else if(input$slider1 == 2014 & input$Werksnummer == "1132"){
      Y2014_1132
    }
    else if(input$slider1 == 2014 & input$Werksnummer == "1141"){
      Y2014_1141
    }
    else if(input$slider1 == 2015 & input$Werksnummer == "1011"){
      Y2015_1011
    }
    else if(input$slider1 == 2015 & input$Werksnummer == "1021"){
      Y2015_1021
    }
    else if(input$slider1 == 2015 & input$Werksnummer == "1031"){
      Y2015_1031
    }
    else if(input$slider1 == 2015 & input$Werksnummer == "1041"){
      Y2015_1041
    }
    else if(input$slider1 == 2015 & input$Werksnummer == "1041"){
      Y2015_1041
    }
    else if(input$slider1 == 2015 & input$Werksnummer == "1051"){
      Y2015_1051
    }
    else if(input$slider1 == 2015 & input$Werksnummer == "1061"){
      Y2015_1061
    }
    else if(input$slider1 == 2015 & input$Werksnummer == "1071"){
      Y2015_1071
    }
    else if(input$slider1 == 2015 & input$Werksnummer == "1072"){
      Y2015_1072
    }
    else if(input$slider1 == 2015 & input$Werksnummer == "1081"){
      Y2015_1081
    }
    else if(input$slider1 == 2015 & input$Werksnummer == "1082"){
      Y2015_1082
    }
    else if(input$slider1 == 2015 & input$Werksnummer == "1091"){
      Y2015_1091
    }
    else if(input$slider1 == 2015 & input$Werksnummer == "1092"){
      Y2015_1092
    }
    else if(input$slider1 == 2015 & input$Werksnummer == "1111"){
      Y2015_1111
    }
   else if(input$slider1 == 2015 & input$Werksnummer == "1101"){
      Y2015_1101
   }
    else if(input$slider1 == 2015 & input$Werksnummer == "1131"){
      Y2015_1131
    }
    else if(input$slider1 == 2015 & input$Werksnummer == "1132"){
      Y2015_1132
    }
    else if(input$slider1 == 2015 & input$Werksnummer == "1141"){
      Y2015_1141
    }
    else if(input$slider1 == 2016 & input$Werksnummer == "1011"){
      Y2016_1011
    }
    else if(input$slider1 == 2016 & input$Werksnummer == "1021"){
      Y2016_1021
    }
    else if(input$slider1 == 2016 & input$Werksnummer == "1031"){
      Y2016_1031
    }
    else if(input$slider1 == 2016 & input$Werksnummer == "1041"){
      Y2016_1041
    }
    else if(input$slider1 == 2016 & input$Werksnummer == "1041"){
      Y2016_1041
    }
    else if(input$slider1 == 2016 & input$Werksnummer == "1051"){
      Y2016_1051
    }
    else if(input$slider1 == 2016 & input$Werksnummer == "1061"){
      Y2016_1061
    }
    else if(input$slider1 == 2016 & input$Werksnummer == "1071"){
      Y2016_1071
    }
    else if(input$slider1 == 2016 & input$Werksnummer == "1072"){
      Y2016_1072
    }
    else if(input$slider1 == 2016 & input$Werksnummer == "1081"){
      Y2016_1081
    }
    else if(input$slider1 == 2016 & input$Werksnummer == "1082"){
      Y2016_1082
    }
    else if(input$slider1 == 2016 & input$Werksnummer == "1091"){
      Y2016_1091
    }
    else if(input$slider1 == 2016 & input$Werksnummer == "1092"){
      Y2016_1092
    }
    else if(input$slider1 == 2016 & input$Werksnummer == "1101"){
      Y2016_1101
    }
    else if(input$slider1 == 2016 & input$Werksnummer == "1111"){
      Y2016_1111
    }
    else if(input$slider1 == 2016 & input$Werksnummer == "1132"){
      Y2016_1132
    }
    else if(input$slider1 == 2016 & input$Werksnummer == "1141"){
      Y2016_1141
    }
  })
    #From here on we Integrate the line Diagramms

    output$plot2 <- renderPlotly({
    
    if(input$slider1 == 2008 & input$Komponente == "K4"){
      Y2008_K4_
    }
    else if(input$slider1 == 2008 & input$Komponente == "K5"){
      Y2008_K5_
    }
    else if(input$slider1 == 2008 & input$Komponente == "K6"){
      Y2008_K6_
    }
    else if(input$slider1 == 2008 & input$Komponente == "K7"){
      Y2008_K7_
    }
    else if(input$slider1 == 2008 & input$Komponente == "K3SG1"){
      Y2008_K3SG1_
    }
    else if(input$slider1 == 2008 & input$Komponente == "K3SG2"){
      Y2008_K3SG2_
    }
    else if(input$slider1 == 2008 & input$Komponente == "K3AG1"){
      Y2008_K3AG1_
    }
    else if(input$slider1 == 2008 & input$Komponente == "K3AG2"){
      Y2008_K3AG2_
    }
    else if(input$slider1 == 2008 & input$Komponente == "K2ST1"){
      Y2008_K2ST1_
    }
    else if(input$slider1 == 2008 & input$Komponente == "K2ST2"){
      Y2008_K2ST2_
    }
    else if(input$slider1 == 2008 & input$Komponente == "K2LE2"){
      Y2008_K2LE2_
    }
    else if(input$slider1 == 2008 & input$Komponente == "K2LE1"){
      Y2008_K2LE1_
    }
    else if(input$slider1 == 2008 & input$Komponente == "K1DI2"){
      Y2008_K1DI2_
    }
    else if(input$slider1 == 2008 & input$Komponente == "K1DI1"){
      Y2008_K1DI1_
    }
    else if(input$slider1 == 2008 & input$Komponente == "K1BE1"){
      Y2008_K1BE1_
    }
    else if(input$slider1 == 2008 & input$Komponente == "K1BE2"){
      Y2008_K1BE2_
    }
    else if(input$slider1 == 2009 & input$Komponente == "K4"){
      Y2009_K4_
    }
    else if(input$slider1 == 2009 & input$Komponente == "K5"){
      Y2009_K5_
    }
    else if(input$slider1 == 2009 & input$Komponente == "K6"){
      Y2009_K6_
    }
    else if(input$slider1 == 2009 & input$Komponente == "K7"){
      Y2009_K7_
    }
    else if(input$slider1 == 2009 & input$Komponente == "K3SG2"){
      Y2009_K3SG2_
    }
      else if(input$slider1 == 2009 & input$Komponente == "K3SG1"){
      Y2009_K3SG1_
    }
    else if(input$slider1 == 2009 & input$Komponente == "K3AG1"){
      Y2009_K3AG1_
    }
    else if(input$slider1 == 2009 & input$Komponente == "K3AG2"){
      Y2009_K3AG2_
    }
    else if(input$slider1 == 2009 & input$Komponente == "K2ST1"){
      Y2009_K2ST1_
    }
    else if(input$slider1 == 2009 & input$Komponente == "K2ST2"){
      Y2009_K2ST2_
    }
    else if(input$slider1 == 2009 & input$Komponente == "K2LE2"){
      Y2009_K2LE2_
    }
    else if(input$slider1 == 2009 & input$Komponente == "K2LE1"){
      Y2009_K2LE1_
    }
    else if(input$slider1 == 2009 & input$Komponente == "K1DI2"){
      Y2009_K1DI2_
    }
    else if(input$slider1 == 2009 & input$Komponente == "K1DI1"){
      Y2009_K1DI1_
    }
    else if(input$slider1 == 2009 & input$Komponente == "K1BE1"){
      Y2009_K1BE1_
    }
    else if(input$slider1 == 2009 & input$Komponente == "K1BE2"){
      Y2009_K1BE2_
    }
     else if(input$slider1 == 2010 & input$Komponente == "K4"){
      Y2010_K4_
    }
    else if(input$slider1 == 2010 & input$Komponente == "K5"){
      Y2010_K5_
    }
    else if(input$slider1 == 2010 & input$Komponente == "K6"){
      Y2010_K6_
    }
    else if(input$slider1 == 2010 & input$Komponente == "K7"){
      Y2010_K7_
    }
    else if(input$slider1 == 2010 & input$Komponente == "K3SG2"){
      Y2010_K3SG2_
    }
      else if(input$slider1 == 2010 & input$Komponente == "K3SG1"){
      Y2010_K3SG1_
    }
    else if(input$slider1 == 2010 & input$Komponente == "K3AG1"){
      Y2010_K3AG1_
    }
    else if(input$slider1 == 2010 & input$Komponente == "K3AG2"){
      Y2010_K3AG2_
    }
    else if(input$slider1 == 2010 & input$Komponente == "K2ST1"){
      Y2010_K2ST1_
    }
    else if(input$slider1 == 2010 & input$Komponente == "K2ST2"){
      Y2010_K2ST2_
    }
    else if(input$slider1 == 2010 & input$Komponente == "K2LE2"){
      Y2010_K2LE2_
    }
    else if(input$slider1 == 2010 & input$Komponente == "K2LE1"){
      Y2010_K2LE1_
    }
    else if(input$slider1 == 2010 & input$Komponente == "K1DI2"){
      Y2010_K1DI2_
    }
    else if(input$slider1 == 2010 & input$Komponente == "K1DI1"){
      Y2010_K1DI1_
    }
    else if(input$slider1 == 2010 & input$Komponente == "K1BE1"){
      Y2010_K1BE1_
    }
    else if(input$slider1 == 2010 & input$Komponente == "K1BE2"){
      Y2010_K1BE2_
    }
      else if(input$slider1 == 2011 & input$Komponente == "K4"){
      Y2011_K4_
    }
    else if(input$slider1 == 2011 & input$Komponente == "K5"){
      Y2011_K5_
    }
    else if(input$slider1 == 2011 & input$Komponente == "K6"){
      Y2011_K6_
    }
    else if(input$slider1 == 2011 & input$Komponente == "K7"){
      Y2011_K7_
    }
    else if(input$slider1 == 2011 & input$Komponente == "K3SG2"){
      Y2011_K3SG2_
    }
      else if(input$slider1 == 2011 & input$Komponente == "K3SG1"){
      Y2011_K3SG1_
    }
    else if(input$slider1 == 2011 & input$Komponente == "K3AG1"){
      Y2011_K3AG1_
    }
    else if(input$slider1 == 2011 & input$Komponente == "K3AG2"){
      Y2011_K3AG2_
    }
    else if(input$slider1 == 2011 & input$Komponente == "K2ST1"){
      Y2011_K2ST1_
    }
    else if(input$slider1 == 2011 & input$Komponente == "K2ST2"){
      Y2011_K2ST2_
    }
    else if(input$slider1 == 2011 & input$Komponente == "K2LE2"){
      Y2011_K2LE2_
    }
    else if(input$slider1 == 2011 & input$Komponente == "K2LE1"){
      Y2011_K2LE1_
    }
    else if(input$slider1 == 2011 & input$Komponente == "K1DI2"){
      Y2011_K1DI2_
    }
    else if(input$slider1 == 2011 & input$Komponente == "K1DI1"){
      Y2011_K1DI1_
    }
    else if(input$slider1 == 2011 & input$Komponente == "K1BE1"){
      Y2011_K1BE1_
    }
    else if(input$slider1 == 2011 & input$Komponente == "K1BE2"){
      Y2011_K1BE2_
    }
      else if(input$slider1 == 2012 & input$Komponente == "K4"){
      Y2012_K4_
    }
    else if(input$slider1 == 2012 & input$Komponente == "K5"){
      Y2012_K5_
    }
    else if(input$slider1 == 2012 & input$Komponente == "K6"){
      Y2012_K6_
    }
    else if(input$slider1 == 2012 & input$Komponente == "K7"){
      Y2012_K7_
    }
    else if(input$slider1 == 2012 & input$Komponente == "K3SG2"){
      Y2012_K3SG2_
    }
      else if(input$slider1 == 2012 & input$Komponente == "K3SG1"){
      Y2012_K3SG1_
    }
    else if(input$slider1 == 2012 & input$Komponente == "K3AG1"){
      Y2012_K3AG1_
    }
    else if(input$slider1 == 2012 & input$Komponente == "K3AG2"){
      Y2012_K3AG2_
    }
    else if(input$slider1 == 2012 & input$Komponente == "K2ST1"){
      Y2012_K2ST1_
    }
    else if(input$slider1 == 2012 & input$Komponente == "K2ST2"){
      Y2012_K2ST2_
    }
    else if(input$slider1 == 2012 & input$Komponente == "K2LE2"){
      Y2012_K2LE2_
    }
    else if(input$slider1 == 2012 & input$Komponente == "K2LE1"){
      Y2012_K2LE1_
    }
    else if(input$slider1 == 2012 & input$Komponente == "K1DI2"){
      Y2012_K1DI2_
    }
    else if(input$slider1 == 2012 & input$Komponente == "K1DI1"){
      Y2012_K1DI1_
    }
    else if(input$slider1 == 2012 & input$Komponente == "K1BE1"){
      Y2012_K1BE1_
    }
    else if(input$slider1 == 2012 & input$Komponente == "K1BE2"){
      Y2012_K1BE2_
    }
      else if(input$slider1 == 2013 & input$Komponente == "K4"){
      Y2013_K4_
    }
    else if(input$slider1 == 2013 & input$Komponente == "K5"){
      Y2013_K5_
    }
    else if(input$slider1 == 2013 & input$Komponente == "K6"){
      Y2013_K6_
    }
    else if(input$slider1 == 2013 & input$Komponente == "K7"){
      Y2013_K7_
    }
    else if(input$slider1 == 2013 & input$Komponente == "K3SG2"){
      Y2013_K3SG2_
    }
      else if(input$slider1 == 2013 & input$Komponente == "K3SG1"){
      Y2013_K3SG1_
    }
    else if(input$slider1 == 2013 & input$Komponente == "K3AG1"){
      Y2013_K3AG1_
    }
    else if(input$slider1 == 2013 & input$Komponente == "K3AG2"){
      Y2013_K3AG2_
    }
    else if(input$slider1 == 2013 & input$Komponente == "K2ST1"){
      Y2013_K2ST1_
    }
    else if(input$slider1 == 2013 & input$Komponente == "K2ST2"){
      Y2013_K2ST2_
    }
    else if(input$slider1 == 2013 & input$Komponente == "K2LE2"){
      Y2013_K2LE2_
    }
    else if(input$slider1 == 2013 & input$Komponente == "K2LE1"){
      Y2013_K2LE1_
    }
    else if(input$slider1 == 2013 & input$Komponente == "K1DI2"){
      Y2013_K1DI2_
    }
    else if(input$slider1 == 2013 & input$Komponente == "K1DI1"){
      Y2013_K1DI1_
    }
    else if(input$slider1 == 2013 & input$Komponente == "K1BE1"){
      Y2013_K1BE1_
    }
    else if(input$slider1 == 2013 & input$Komponente == "K1BE2"){
      Y2013_K1BE2_
    }
      else if(input$slider1 == 2014 & input$Komponente == "K4"){
      Y2014_K4_
    }
    else if(input$slider1 == 2014 & input$Komponente == "K5"){
      Y2014_K5_
    }
    else if(input$slider1 == 2014 & input$Komponente == "K6"){
      Y2014_K6_
    }
    else if(input$slider1 == 2014 & input$Komponente == "K7"){
      Y2014_K7_
    }
    else if(input$slider1 == 2014 & input$Komponente == "K3SG2"){
      Y2014_K3SG2_
    }
      else if(input$slider1 == 2014 & input$Komponente == "K3SG1"){
      Y2014_K3SG1_
    }
    else if(input$slider1 == 2014 & input$Komponente == "K3AG1"){
      Y2014_K3AG1_
    }
    else if(input$slider1 == 2014 & input$Komponente == "K3AG2"){
      Y2014_K3AG2_
    }
    else if(input$slider1 == 2014 & input$Komponente == "K2ST1"){
      Y2014_K2ST1_
    }
    else if(input$slider1 == 2014 & input$Komponente == "K2ST2"){
      Y2014_K2ST2_
    }
    else if(input$slider1 == 2014 & input$Komponente == "K2LE2"){
      Y2014_K2LE2_
    }
    else if(input$slider1 == 2014 & input$Komponente == "K2LE1"){
      Y2014_K2LE1_
    }
    else if(input$slider1 == 2014 & input$Komponente == "K1DI2"){
      Y2014_K1DI2_
    }
    else if(input$slider1 == 2014 & input$Komponente == "K1DI1"){
      Y2014_K1DI1_
    }
    else if(input$slider1 == 2014 & input$Komponente == "K1BE1"){
      Y2014_K1BE1_
    }
    else if(input$slider1 == 2014 & input$Komponente == "K1BE2"){
      Y2014_K1BE2_
    }
      else if(input$slider1 == 2015 & input$Komponente == "K4"){
      Y2015_K4_
    }
    else if(input$slider1 == 2015 & input$Komponente == "K5"){
      Y2015_K5_
    }
    else if(input$slider1 == 2015 & input$Komponente == "K6"){
      Y2015_K6_
    }
    else if(input$slider1 == 2015 & input$Komponente == "K7"){
      Y2015_K7_
    }
    else if(input$slider1 == 2015 & input$Komponente == "K3SG2"){
      Y2015_K3SG2_
    }
      else if(input$slider1 == 2015 & input$Komponente == "K3SG1"){
      Y2015_K3SG1_
    }
    else if(input$slider1 == 2015 & input$Komponente == "K3AG1"){
      Y2015_K3AG1_
    }
    else if(input$slider1 == 2015 & input$Komponente == "K3AG2"){
      Y2015_K3AG2_
    }
    else if(input$slider1 == 2015 & input$Komponente == "K2ST1"){
      Y2015_K2ST1_
    }
    else if(input$slider1 == 2015 & input$Komponente == "K2ST2"){
      Y2015_K2ST2_
    }
    else if(input$slider1 == 2015 & input$Komponente == "K2LE2"){
      Y2015_K2LE2_
    }
    else if(input$slider1 == 2015 & input$Komponente == "K2LE1"){
      Y2015_K2LE1_
    }
    else if(input$slider1 == 2015 & input$Komponente == "K1DI2"){
      Y2015_K1DI2_
    }
    else if(input$slider1 == 2015 & input$Komponente == "K1DI1"){
      Y2015_K1DI1_
    }
    else if(input$slider1 == 2015 & input$Komponente == "K1BE1"){
      Y2015_K1BE1_
    }
    else if(input$slider1 == 2015 & input$Komponente == "K1BE2"){
      Y2015_K1BE2_
    }
      else if(input$slider1 == 2016 & input$Komponente == "K4"){
      Y2016_K4_
    }
    else if(input$slider1 == 2016 & input$Komponente == "K5"){
      Y2016_K5_
    }
    else if(input$slider1 == 2016 & input$Komponente == "K6"){
      Y2016_K6_
    }
    else if(input$slider1 == 2016 & input$Komponente == "K7"){
      Y2016_K7_
    }
    else if(input$slider1 == 2016 & input$Komponente == "K3SG2"){
      Y2016_K3SG2_
    }
      else if(input$slider1 == 2016 & input$Komponente == "K3SG1"){
      Y2016_K3SG1_
    }
    else if(input$slider1 == 2016 & input$Komponente == "K3AG1"){
      Y2016_K3AG1_
    }
    else if(input$slider1 == 2016 & input$Komponente == "K3AG2"){
      Y2016_K3AG2_
    }
    else if(input$slider1 == 2016 & input$Komponente == "K2ST1"){
      Y2016_K2ST1_
    }
    else if(input$slider1 == 2016 & input$Komponente == "K2ST2"){
      Y2016_K2ST2_
    }
    else if(input$slider1 == 2016 & input$Komponente == "K2LE2"){
      Y2016_K2LE2_
    }
    else if(input$slider1 == 2016 & input$Komponente == "K2LE1"){
      Y2016_K2LE1_
    }
    else if(input$slider1 == 2016 & input$Komponente == "K1DI2"){
      Y2016_K1DI2_
    }
    else if(input$slider1 == 2016 & input$Komponente == "K1DI1"){
      Y2016_K1DI1_
    }
    else if(input$slider1 == 2016 & input$Komponente == "K1BE1"){
      Y2016_K1BE1_
    }
    else if(input$slider1 == 2016 & input$Komponente == "K1BE2"){
      Y2016_K1BE2_
    }
      
      
    
   })
  
}

shinyApp(ui, server,options =  list(height = 1080,width=1080))

```
